---
title: "Effect of cholinergic stimulation on CA1 and CA3 PSD"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(include=TRUE, collapse=TRUE, warning=FALSE, echo=FALSE)
```

Effects of the laser activation on the signal recorded in baseline conditions.

```{r include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)
library(ggpubr)
select = dplyr::select

source('laser_stats.R')
source('plotting_params.R')
source('psd_analysis.R')
source('psd_fitting.R')
```


```{r include=FALSE}
img_dir = paste0('/home/prez/tmp/ymaze_chat_x_ai32/img_gen/', experiment_name)
experiment_name = 'baseline'
diode.signal = TRUE
data_dir = paste0('/mnt/DATA/chat_ripples/', experiment_name)

if (diode.signal) {
  psddf = read_csv(paste(data_dir, 'trial_results_gfp', 'welch_psd_table_diode_th6.csv', sep='/'))
} else {
  psddf = read_csv(paste(data_dir,'trial_results_gfp', 'welch_psd_table_th6.csv', sep='/'))
}
psddf$animal = as.factor(psddf$animal)
psddf$channel = as.factor(psddf$channel)
psddf$laserOn = as.factor(psddf$laserOn)

psddf = psddf %>%
  dplyr::mutate(trial_id=paste(date, animal, trial ,sep='_'))
psddf$trial_id = as.factor(psddf$trial_id)

freq.bands.df = data.frame(
  band=c('theta', 'slow gamma'),
  xmin=c(5, 25),
  xmax=c(11, 45)
)
```

# Effects on the signal spectrum
Number of trials per animal
```{r}
psddf %>% group_by(animal) %>%
  dplyr::summarise(ntrials=length(unique(trial_id))) %>%
  dplyr::summarise(mean(ntrials), sem(ntrials),)
```

## PSD ratio
Replicates Vandecasteele (2014), but the PSD ratios problematic as reflect changes in background spectrum

Ratios per animal
```{r}
psd.molten = melt.freq.bands(psddf, extra.id.vars = c('state'))
psd.ratio.df = calc.freq.band.ratio(psd.molten)

animal.psd.ratio = psd.ratio.df %>%
  dplyr::group_by(animal, band_name, band_start_freq, channelLocation, state) %>%
  dplyr::summarise(ratio.mean=mean(power.ratio.change, na.rm=TRUE),
                   ratio.sem=sem(power.ratio.change))
  
axis.breaks=c(1:9,seq(10,100,10),200)
axis.labels=rep('', length(axis.breaks))
axis.labels[1]=1
axis.labels[10]=10
axis.labels[19]=100

animal.psd.ratio %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, group=animal, y=ratio.mean, color=animal)) + 
  geom_ribbon(aes(x=band_start_freq, group=animal, ymin=ratio.mean-ratio.sem, ymax=ratio.mean+ratio.sem),
              alpha=0.1) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-1, ymax=5, alpha=0.05, fill='grey10') +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  geom_hline(yintercept=1, linetype='dashed') +
  facet_grid(state ~ channelLocation) +
  xlab('Frequency (Hz)') +
  ylab('LFP power ratio') +
  gtheme +
  theme(legend.position = 'top')
```

Mean ratio
```{r}
channel.psd.ratio = psd.ratio.df %>%
  dplyr::group_by(band_name, band_start_freq, channelLocation, state) %>%
  dplyr::summarise(ratio.mean=mean(power.ratio.change, na.rm=TRUE),
                   ratio.sem=sem(power.ratio.change))
  
channel.psd.ratio %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, group=channelLocation, y=ratio.mean, colour=channelLocation)) + 
  geom_ribbon(aes(x=band_start_freq, group=channelLocation, ymin=ratio.mean-ratio.sem, ymax=ratio.mean+ratio.sem),
              alpha=0.1) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-1, ymax=5, alpha=0.05, fill='grey10') +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  geom_hline(yintercept=1, linetype='dashed') +
  facet_grid(state ~ channelLocation) +
  xlab('Frequency (Hz)') +
  ylab('LFP power ratio') +
  gtheme +
  theme(legend.position = 'none')
```

# PSD and background spectrum fit
```{r include = FALSE}
animals.psd = psd.molten %>%
  filter(stage_desc %in% c('stim', 'before_stim')) %>%
  group_by(channelLocation, animal, laserOn, stage_desc, band_start_freq) %>%
  dplyr::summarise(sem.power = sem(log(band_power)), 
                   band_power = mean(log(band_power)))

joined.psd.fit.df = map_dfr(unique(animals.psd$animal), ~ {
  animal.psd = filter(animals.psd, animal == .x)
  animal.psd$name = 'model'
  animal.fit.low.freq = calc.animal.band.fit.df(animal.psd, c(2, 20)) %>%
    dplyr::mutate(animal = .x, name = paste(name, 'low_freq', sep='_'))
  animal.fit.high.freq = calc.animal.band.fit.df(animal.psd, c(15, 150)) %>%
    dplyr::mutate(animal = .x, name = paste(name, 'high_freq', sep='_'))
  bind_rows(animal.psd, animal.fit.low.freq, animal.fit.high.freq)
})
```

```{r}
joined.psd.fit.df %>%
  #filter(animal == 'BS') %>%
  dplyr::mutate(name_laser=paste(name, laserOn, sep='_')) %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, y=band_power, 
                group=name_laser, color=laserOn, linetype=name)) +
  geom_ribbon(aes(x=band_start_freq, y=band_power, 
                  group=name_laser, fill=laserOn,
                  ymin=band_power - sem.power, ymax=band_power + sem.power), 
              alpha=0.2) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-20, ymax=-5, alpha=0.05, fill='grey10') +
  facet_wrap(animal ~ channelLocation, scales = 'free', ncol = 4) +
  scale_x_log10(limits=c(2,200), breaks=axis.breaks, labels=axis.labels) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  #ylim(-18.3,-7.2) +
  #scale_y_continuous(breaks=c(-15,-10))+
  gtheme +
  theme(legend.position = 'top') +
  scale_linetype_manual(values=c('dotted', 'dotted', 'solid')) +
  xlab('Frequency (Hz)') + ylab('Log power')

#ggsave(file=paste0(img_dir, '/', '2_psd_mean.pdf'), 
#       width=13.5, height=6.5, unit='cm', dpi=300, device=cairo_pdf)
 
ggsave(file=paste0(img_dir, '/', '2_psd_mean_all.pdf'), 
       width=15, height=14, unit='cm', dpi=300, device=cairo_pdf)
```


```{r}
plotted.lowfreq.fit = filter(joined.psd.fit.df, name != 'bg_high_freq')
bind_rows(animals.psd, plotted.lowfreq.fit) %>%
  #filter(animal == 'BS') %>%
  filter(animal == 'BD') %>%
  dplyr::mutate(name_laser=paste(name, laserOn, sep='_')) %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, y=band_power, 
                group=name_laser, color=laserOn, linetype=name)) +
  geom_ribbon(aes(x=band_start_freq, y=band_power, 
                  group=name_laser, fill=laserOn,
                  ymin=band_power - sem.power, ymax=band_power + sem.power), 
              alpha=0.2) +
  scale_x_log10(limits=c(2,20), breaks=axis.breaks, labels=axis.labels) +
  ylim(-13,-7.1)+
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  scale_linetype_manual(values=c('dashed', 'solid')) +
  facet_grid(. ~ channelLocation, scales = 'free') +
  gtheme +
  theme(legend.position = 'none') +
  xlab('Frequency (Hz)') + ylab('Log power')
ggsave(file=paste0(img_dir, '/', '2_psd_fit_inset.pdf'), 
       width=8, height=8, unit='cm', dpi=300, device=cairo_pdf)
```


```{r}
trial.molten.psd = psd.molten %>%
  filter(state != 'scopolamine') %>%
  filter(animal == 'BD') %>%
  dplyr::mutate(trial_id_laser = paste(trial_id, laserOn, sep='_'))

library(permute)
sample.n.trials = function(df, n=5) {
   trial.ids = unique(df$trial_id)
   #set.seed(42)
   trial.ids = trial.ids[permute::shuffle(length(trial.ids))]
   n = min(n, length(trial.ids))
   trial.ids = trial.ids[1:n]
   filter(df, trial_id %in% trial.ids)
}

bind_rows(
  sample.n.trials(filter(trial.molten.psd, stage_desc == 'before_stim'), n=10),
  sample.n.trials(filter(trial.molten.psd, stage_desc == 'stim'), n=10)
) %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, y=log(band_power), group=trial_id_laser, color=laserOn), size=0.5*px2pt) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-25, ymax=-5, alpha=0.05, fill='grey10') +
  facet_grid(animal ~ channelLocation, scales = 'free') +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  #xlim(c(3,80)) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  gtheme +
  xlab('Frequency (Hz)') + ylab('Power (log)')

ggsave(file=paste0(img_dir, '/', '2_psd_indiv_traces.pdf'), 
       width=12.5, height=6, unit='cm', dpi=300, device=cairo_pdf)
```


# Coherence
```{r}
#wcoh.df = read_csv(paste(data_dir, 'ripple_coherence_table_diode.csv', sep='/'))
wcoh.df = read_csv(paste(data_dir, 'trial_results', 'coherence_table_diode.csv', sep='/'))
wcoh.df$animal = as.factor(wcoh.df$animal)
wcoh.df$laserOn = as.factor(wcoh.df$laserOn)
wcoh.df = wcoh.df %>%
  dplyr::mutate(trial_id=paste(date, animal, trial ,sep='_'))
wcoh.df$trial_id = as.factor(wcoh.df$trial_id)
wcoh.df$channelLocation = 'CA1-CA3'
```

```{r}
wcoh.molten = melt.freq.bands(wcoh.df, extra.id.vars = c(), psd.vars.prefix='all_coh_', freq.bands = c(exp(seq(0.1, 5.6, by=0.07))))
```

```{r}
animal.wcoh.df = wcoh.molten %>%
  dplyr::group_by(animal, band_name, band_start_freq, laserOn) %>%
  dplyr::summarise(power.mean=mean(band_power, na.rm=TRUE),
                   power.sem=sem(band_power))

animal.wcoh.df %>%
  dplyr::mutate(animal_laser=paste(animal, laserOn, sep='_')) %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, group=animal_laser, y=power.mean, color=laserOn)) + 
  geom_ribbon(aes(x=band_start_freq, group=animal_laser, ymin=power.mean-power.sem, ymax=power.mean+power.sem),
              alpha=0.1) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-1, ymax=5, alpha=0.05, fill='grey10') +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  xlab('Frequency (Hz)') +
  ylab('Coherence') +
  facet_wrap(animal ~ ., ncol = 3) +
  gtheme +
  theme(legend.position = 'top')
```
Coherence not changed by the laser.
```{r}
m.full = lmerTest::lmer(log(abs(coh_theta)) ~ laserOn + (1 + laserOn | animal), data=wcoh.df, REML = TRUE) 
summary(m.full)
plot.model.diagnostics(m.full, wcoh.df$animal, wcoh.df$laserOn)
coef(m.full)$animal
anova(m.full, refit=FALSE, ddf='Satterthwaite')
```


# PSD fit
Fit background with FOOOF and check quality
```{r}
fit.psd.df = fit.background.df(psd.molten, freq.bands.df, c(15, 150), fit.knee = FALSE)

summary(fit.psd.df$fit_error)
```


Aperiodicity reduced:
Background offset reduced, but slope also increased -> PSD starts lower but decreases less with freq,
```{r}
g.bac.auc = plot.laser.change(fit.psd.df, background_auc) + ylab('Background spectrum AUC')
g.bac.auc
calc.laser.fixed.effects(subset(fit.psd.df, channelLocation == 'CA1'), background_auc)
calc.laser.fixed.effects(subset(fit.psd.df, channelLocation == 'CA3'), background_auc)
```
```{r}
fit.psd.df %>% group_by(channelLocation, laserOn) %>% dplyr::summarise(mean(background_auc, na.rm=T), sem(background_auc))
```

## Slow Gamma
Count of trials with slow gamma:
```{r}
var = quo(pow_slow_gamma)
pct.theta.oscillating = group_by(fit.psd.df, channelLocation, animal, laserOn) %>%
  dplyr::summarise(pct.oscillating=sum(!is.na(!!var)) / n())
pct.theta.oscillating
ca.subset = subset(pct.theta.oscillating, channelLocation == 'CA1')
t.test(subset(ca.subset, laserOn==0)$pct.oscillating,
       subset(ca.subset, laserOn==1)$pct.oscillating, 
       paired=TRUE)
group_by(pct.theta.oscillating, channelLocation, laserOn) %>% dplyr::summarise(mean(pct.oscillating), sem(pct.oscillating))
```

Significant increase in slow gamma
```{r}
var = quo(pow_slow_gamma)
fit.sgamma.present = fit.psd.df %>%
  dplyr::mutate(!!var := ifelse(is.na(!!var), 0, !!var))
g.sgamma.pow = plot.laser.change(fit.psd.df, !!var) + ylab('Relative Slow Gamma Power (25 - 45 Hz)')
g.sgamma.pow
calc.laser.fixed.effects(subset(fit.sgamma.present, channelLocation == 'CA1'), !!var)
calc.laser.fixed.effects(subset(fit.sgamma.present, channelLocation == 'CA3'), !!var)

fit.psd.df %>% group_by(channelLocation, laserOn) %>% dplyr::summarise(mean(!!var, na.rm=T), sem(!!var))
```
SGamma central frequency when the laser on...
```{r}
peak_var = quo(peak_slow_gamma)

filter(fit.psd.df, !is.na(!!peak_var)) %>%
  group_by(animal, channelLocation, laserOn) %>% 
  dplyr::summarise(peak.mean = mean(!!peak_var),
                   peak.median = median(!!peak_var),
                   peak.sem = sem(!!peak_var)) %>% 
  dplyr::group_by(channelLocation, laserOn) %>%
  dplyr::summarise(mean(peak.mean), sem(peak.mean))

plot.laser.change(fit.psd.df, !!peak_var) + ylab('Central Slow Gamma frequency (Hz)')
calc.laser.fixed.effects(filter(fit.sgamma.present, channelLocation == 'CA1', !is.na(!!peak_var)), !!peak_var)
calc.laser.fixed.effects(filter(fit.sgamma.present, channelLocation == 'CA3', !is.na(!!peak_var)), !!peak_var)
```
## Theta
Fit background with FOOOF and check quality
```{r}
fit.psd.df = fit.background.df(psd.molten, freq.bands.df, c(2, 20), fit.knee = FALSE)

summary(fit.psd.df$fit_error)
```

Count of trials with theta:
```{r}
var = quo(pow_theta)
pct.theta.oscillating = group_by(fit.psd.df, channelLocation, animal, laserOn) %>%
  dplyr::summarise(pct.oscillating=sum(!is.na(!!var)) / n())
pct.theta.oscillating
ca.subset = subset(pct.theta.oscillating, channelLocation == 'CA1')
t.test(subset(ca.subset, laserOn==0)$pct.oscillating,
       subset(ca.subset, laserOn==1)$pct.oscillating, 
       paired=TRUE)
group_by(pct.theta.oscillating, channelLocation, laserOn) %>% dplyr::summarise(mean(pct.oscillating), sem(pct.oscillating))
```

Significant increase in pow theta.
```{r}
var = quo(pow_theta)
fit.theta.present = fit.psd.df %>%
  filter(!is.na(!!var))

g.theta.pow = plot.laser.change(fit.psd.df, !!var) + ylab('Relative Theta Power (5 - 11 Hz)')
g.theta.pow
calc.laser.fixed.effects(filter(fit.theta.present, channelLocation == 'CA1'), !!var)
calc.laser.fixed.effects(filter(fit.theta.present, channelLocation == 'CA3'), !!var)
fit.psd.df %>% group_by(channelLocation, laserOn) %>% dplyr::summarise(mean(!!var, na.rm=T), sem(!!var))
```

Lower theta central frequency when the laser on
```{r}
peak_var = quo(peak_theta)
filter(fit.psd.df, !is.na(!!peak_var)) %>%
  group_by(animal, channelLocation, laserOn) %>%
  dplyr::summarise(peak_theta.mean = mean(!!peak_var),
                   peak_theta.median = median(!!peak_var),
                   peak_theta.sem = sem(!!peak_var)) %>%
  dplyr::group_by(channelLocation, laserOn) %>%
  dplyr::summarise(mean(peak_theta.mean), sem(peak_theta.mean))

plot.laser.change(fit.psd.df, !!peak_var) + ylab('Central Theta frequency (Hz)')
calc.laser.fixed.effects( filter(fit.psd.df, !is.na(!!peak_var), channelLocation == 'CA1'), !!peak_var)
calc.laser.fixed.effects( filter(fit.psd.df, !is.na(!!peak_var), channelLocation == 'CA3'), !!peak_var)
```

```{r}
plot_grid(g.bac.auc, g.theta.pow, g.sgamma.pow, ncol=3)
ggsave(file=paste0(img_dir, '/', '2_psd_stats.pdf'), 
       width=12, height=5, unit='cm', dpi=300, device=cairo_pdf)
```

