---
title: "Effect of cholinergic stimulation on CA1 and CA3 ripples"
output:
  html_document:
    df_print: paged
---

Notebook should be run after sleep_psd.Rmd 

```{r include=FALSE}
experiment_name = 'baseline'
diode.signal = TRUE

img_dir = paste0('/home/prez/tmp/ymaze_chat_x_ai32/img_gen/', experiment_name)
source('plotting_params.R')
```

```{r include=FALSE}
data_dir =  '/mnt/DATA/chat_ripples/baseline'
if (diode.signal) {
  input.filename = 'ripples_diode_th7.csv'
} else {
  input.filename = 'ripples_th7.csv'
}

min.swr.freq = 140
ripple.df = bind_rows(
  read_csv(file.path(data_dir, 'trial_results', input.filename)),
  read_csv(file.path(data_dir, 'trial_results_gfp', input.filename)))

ripple.df = ripple.df %>%
  replace_na(list(exp = 'main-effect')) %>%
  dplyr::mutate(trial_id = paste(date, animal, trial, sep='_'),
                exp_animal = paste(exp, animal, sep='_'),
                is.swr=peak_freq >= min.swr.freq)

psddf$exp = as.factor(psddf$exp)
psddf$exp_animal = as.factor(psddf$exp_animal)
ripple.df$animal = as.factor(ripple.df$animal)
ripple.df$channel = as.factor(ripple.df$channel)
ripple.df$laserOn = as.factor(ripple.df$laserOn)
ripple.df$stage_desc = as.factor(ripple.df$stage_desc)
ripple.df$stage_desc = factor(ripple.df$stage_desc, levels=c('before_stim','stim','after_stim'))
```

#Effect of the laser on ripples

Ripples were automatically dected as events of duration 40-350 ms with power in 80-250 Hz band exceeding the threshold of 3 standard deviations.

Example of a detected ripple is shown below
The unprocessed signal is visible on the bottom panel, top panel shows the power in 80-250 Hz band with the marked ripple.


#SWRs peak frequency 
```{r}
ripple.df %>%
  filter(laserOn == 0) %>%
  ggplot() +
  geom_histogram(aes(x=peak_freq, fill=animal, color=animal),  position='identity',alpha=0.2) + 
  facet_grid(exp + animal ~ channelLocation, scales =  'free_y')
```


ripple stats during control
```{r}
metric_name = 'peak_freq'
#metric_name = 'ripple_dur'

filter(ripple.df, !is.na(peak_freq), exp == 'main-effect', laserOn==0, channelLocation == 'CA1')[,metric_name] %>% 
  pull-> ripple_freqs

summary(ripple_freqs)
sem(ripple_freqs)
```

## Laser effect on SWR - mixed effects model
CA1
```{r}
ca1.psddf = filter(psddf, channelLocation == 'CA1', stage_desc != 'after_stim')
m.full = calc.laser.fixed.effects(ca1.psddf, swr_incidence)
plot.samples(ca1.psddf, swr_incidence) + ylab('Ripple incidence (Hz)')
pairwise.post.hoc(m.full)
ggsave(file=paste0(img_dir, '/', '2_sleep_ripples_stats.pdf'), 
       width=4.5, height=5.0, unit='cm', dpi=300, device=cairo_pdf)
```

Median change in ripple incidence per animal
```{r}
swr.diff.pct.df = filter(ca1.psddf, stage_desc != 'after_stim') %>%
  group_by(animal, exp,laserOn, stage_desc) %>% 
    dplyr::summarise(var.median = median(swr_incidence, na.rm=TRUE)) %>%
  reshape2::dcast(exp + animal ~ laserOn) %>%
  dplyr::mutate(diff.pct = (`0` - `1`) / `0` * 100)

swr.diff.pct.df
filter(swr.diff.pct.df, exp=='main-effect', diff.pct < 100) %>%
  dplyr::summarise(mean(diff.pct), sem(diff.pct))

swr.diff.pct.df %>%
  group_by(exp) %>%
  dplyr::summarise(mean(diff.pct), sem(diff.pct))
```

CA1 ripple durations
```{r}
ca1.ripple.df = filter(ripple.df, channelLocation == 'CA1', stage_desc != 'after_stim') 
m.full = calc.laser.fixed.effects(filter(ca1.ripple.df, peak_freq >= 140), log(ripple_dur))

ggplot(filter(ca1.ripple.df, peak_freq >= 140), aes(x=ripple_dur*1000)) +
  geom_histogram(aes(color=laserOn, y=..count.., fill=laserOn), binwidth = 10, alpha=0.5, position='identity') +
  facet_grid(. ~ exp) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  gtheme +
  xlab('Ripple duration (ms)') + ylab('# SWRs')

ggsave(file=file.path(img_dir, '3_ripple_duration.pdf'), 
       width=9, height=5.5, unit='cm', dpi=300, device=cairo_pdf)
```

CA1 ripple peak frequency
```{r}
m.full = calc.laser.fixed.effects(ca1.ripple.df, peak_freq)

ggplot(ca1.ripple.df, aes(x=peak_freq)) +
  geom_histogram(aes(color=laserOn, y=..count.., fill=laserOn), binwidth = 10, alpha=0.5, position='identity') +
  facet_grid(. ~ exp) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  gtheme +
  xlab('Peak frequency (Hz)') + ylab('# Ripples')

ggsave(file=file.path(img_dir, '3_peak_freq.pdf'), 
       width=9, height=5.5, unit='cm', dpi=300, device=cairo_pdf)
```
```{r}
filter(ca1.ripple.df, laserOn == 0, exp=='main-effect', peak_freq >= 140) %>%
  pull(peak_freq) -> X
summary(X)
sem(X)
```

Ripples vs high-gamma events
```{r}
ca1.ripple.df %>%
  dplyr::group_by(exp, channelLocation, is.swr) %>%
  dplyr::summarise(n(), mean(peak_freq), median(peak_freq))
```



Histogram of the ripples over time - the laser active at 30-60 s
```{r include=TRUE}
source('bin_ripples.R')

channel.loc='CA1'

binned.ripple.df = ripple.df %>% 
  filter(channelLocation == channel.loc, exp == 'main-effect') %>%
  filter(is.swr) %>%
  bin.ripples(bin_dur=5)

incidence.summary = binned.ripple.df %>%
  dplyr::group_by(bin_sec, laserOn) %>%
  dplyr::summarise(mincidence = mean(incidence, na.rm = TRUE),
                    incidence.sd = sem(incidence), n=n())

g = ggplot(incidence.summary, aes(x=bin_sec, y=mincidence)) +
  geom_col(fill='white', position=position_dodge(width=-2.5), color='#444444', size=0.5) +
  geom_errorbar(aes(ymin=mincidence - incidence.sd, ymax=mincidence +incidence.sd), width=1.2, color='#444444') +
  ylab('Ripple\nincidence (Hz)') +
  xlab('Time (s)') +
  #scale_color_manual(values = c("grey", "#56B4E9")) +
  scale_x_continuous(breaks=c(0, 30, 60, 90))  +
  #scale_y_continuous(breaks=c(0, 0.2, 0.4)) +
  gtheme +
  theme(legend.position = 'none') 

g
ggsave(file=paste0(img_dir, '/', '3_ripple_incidence_', channel.loc, '.pdf'), 
     width=8.5, height=3, unit='cm', dpi=300, device=cairo_pdf)
```
