---
title: "Effect of cholinergic stimulation on CA1 and CA3 ripples"
output:
  html_document:
    df_print: paged
---

Notebook should be run after sleep_psd.Rmd 

```{r include=FALSE}
experiment_name = 'baseline'
diode.signal = TRUE

img_dir = paste0('/home/prez/tmp/ymaze_chat_x_ai32/img_gen/', experiment_name)
source('plotting_params.R')
```

```{r include=FALSE}
data_dir =  '/mnt/DATA/chat_ripples/baseline'
if (diode.signal) {
  ripple.df = read_csv(paste(data_dir, 'trial_results_gfp', 'ripples_diode_th6.csv', sep='/'))
  
} else {
  ripple.df = read_csv(paste(data_dir, 'trial_results_gfp', 'ripples_th6.csv', sep='/'))
}

ripple.df = ripple.df %>%
  dplyr::mutate(trial_id=paste(date, animal, trial ,sep='_'))

ripple.df$animal = as.factor(ripple.df$animal)
ripple.df$channel = as.factor(ripple.df$channel)
ripple.df$laserOn = as.factor(ripple.df$laserOn)
ripple.df$stage_desc = as.factor(ripple.df$stage_desc)
ripple.df$stage_desc = factor(ripple.df$stage_desc, levels=c('before_stim','stim','after_stim'))
```

#Effect of the laser on ripples

Ripples were automatically dected as events of duration 40-350 ms with power in 80-250 Hz band exceeding the threshold of 3 standard deviations.

Example of a detected ripple is shown below
The unprocessed signal is visible on the bottom panel, top panel shows the power in 80-250 Hz band with the marked ripple.


#SWRs peak frequency 
```{r}
ripple.df %>%
  ggplot() +
  geom_histogram(aes(x=peak_freq, fill=animal, color=animal),  position='identity',alpha=0.2) + 
  facet_grid(animal ~ channelLocation)

```

The detected events have their frequency peak around ~120Hz as expected in CA3.

```{r include=TRUE}
ripple.df %>%
  ggplot() +
  geom_histogram(aes(x=peak_freq, color=laserOn), fill='white', alpha=0.4) +
  scale_x_continuous(breaks=c(100, 120, 140, 160, 180, 200))

```

ripple stats during control
```{r}
metric_name = 'peak_freq'
#metric_name = 'ripple_dur'

filter(ripple.df, !is.na(peak_freq))[,metric_name] %>% 
  pull-> ripple_freqs

summary(ripple_freqs)
sem(ripple_freqs)
```

## Laser effect on SWR - mixed effects model
CA1
```{r}
ca1.psddf = filter(psddf, channelLocation == 'CA1', stage_desc != 'after_stim')
m.full = lmerTest::lmer(swr_incidence ~ laserOn  + (1 + laserOn | animal), data=ca1.psddf, REML = TRUE) 
plot.model.diagnostics(m.full, ca1.psddf$animal, ca1.psddf$laserOn)
summary(m.full)
coef(m.full)$animal
anova(m.full, refit=FALSE, ddf='Satterthwaite')
```

CA3
```{r}
ca3.psddf = filter(psddf, channelLocation == 'CA3', stage_desc != 'after_stim')
m.full = lmerTest::lmer(swr_incidence ~ laserOn + (1 + laserOn | animal), data=ca3.psddf, REML = TRUE) 
plot.model.diagnostics(m.full, ca3.psddf$animal, ca3.psddf$laserOn)
summary(m.full)
coef(m.full)$animal
anova(m.full, refit=FALSE, ddf='Satterthwaite')
```



```{r}
paired.swr.wilcox = function(psddf.all, var.name, cond.name, paired=TRUE) {
  Y = psddf.all %>%
    select(trial_id, ond.name, var.name)
  paired.swr = unstack(Y, formula(paste0(var.name, ' ~ ', cond.name )))
  wilcox.test(paired.swr[[1]], paired.swr[[2]], paired=paired, alternative='greater')
}
```



Paired comparison of ripple incidence during the same trial shows the effect of laser is less prominent in some of the individual awake mice.

# ```{r include=TRUE}
# my.paired.plot(paired.psddf.all, 'swr_incidence') +
#   facet_grid(state ~ .) +
#   ylab('Ripple incidence (Hz)')
# ```
SWR incidence summary
```{r}
stage.name = 'stim'
ca3.psddf %>%
  group_by(animal, stage_desc) %>%
  dplyr::summarise(m.var=mean(swr_incidence)) %>%
  group_by(stage_desc) %>%
  dplyr::summarise(mean(m.var), sem(m.var))

print('CA1')
summary(subset(ca1.psddf, stage_desc == stage.name)$swr_incidence) 
sem(subset(ca1.psddf, stage_desc == stage.name)$swr_incidence) 

print('CA3')
summary(subset(ca3.psddf, stage_desc == stage.name)$swr_incidence) 
sem(subset(ca3.psddf, stage_desc == stage.name)$swr_incidence) 
```


```{r}
# CA3 peak freq
ca3.ripple.df = filter(ripple.df, channelLocation == 'CA1', stage_desc != 'after_stim')
m.full = lmerTest::lmer(peak_freq ~ laserOn + (1 + laserOn | animal), data=ca3.ripple.df, REML = TRUE) 
plot.model.diagnostics(m.full, ca3.ripple.df$animal, ca3.ripple.df$laserOn)
summary(m.full)
coef(m.full)$animal
anova(m.full, refit=FALSE, ddf='Satterthwaite')
```

Detected ripples are shorter during the laser activation
```{r include=TRUE}
ripple.df = ripple.df %>%
  mutate(ripple_dur = end_time-start_sec)

ripple.df %>%
  ggplot() +
  geom_histogram(aes(x=ripple_dur, group=laserOn, col=laserOn, fill=laserOn), alpha=0.5) +
  xlab('Ripple duration (s)') + ylab('#Ripples')

ripple.df %>%
  ggplot() +
  facet_grid(. ~ channelLocation) +
  geom_boxplot(aes(x=animal, y=ripple_dur, col=laserOn)) +
  ylab('Ripple duration (s)') + xlab('Animal')

kruskal.test(ripple_dur~laserOn, data=ripple.df)
```


Histogram of the ripples over time - the laser active at 20-40 s

```{r include=TRUE}
source('bin_ripples.R')

channel.loc='CA1'

binned.ripple.df = ripple.df %>% 
  filter(channelLocation == channel.loc) %>%
  bin.ripples(bin_dur=5)

incidence.summary = binned.ripple.df %>%
  dplyr::group_by(bin_sec, laserOn) %>%
  dplyr::summarise(mincidence = mean(incidence, na.rm = TRUE),
                    incidence.sd = sem(incidence))

g = ggplot(incidence.summary, aes(x=bin_sec, y=mincidence)) +
  geom_col(fill='white', colour='black', position=position_dodge(width=-2.5)) +
  geom_errorbar(aes(ymin=mincidence - incidence.sd, ymax=mincidence +incidence.sd), width=1.2) +
  ylab('Ripple\nincidence (Hz)') +
  xlab('Time (s)') +
  #scale_fill_manual(values = c("grey", "#56B4E9")) +
  scale_x_continuous(breaks=c(30,60))  +
  scale_y_continuous(breaks=c(0, 0.2, 0.4)) +
  gtheme +
  theme(legend.position = 'none') 

g
ggsave(file=paste0(img_dir, '/', '3_ripple_incidence_', channel.loc, '.pdf'), 
     width=9.3, height=3, unit='cm', dpi=300, device=cairo_pdf)
```

Decrease in ripples per animal
```{r}
swr.baseline.summary = filter(psddf, stage_desc != 'after_stim') %>%
  group_by(animal, laserOn, stage_desc, state, channelLocation) %>% 
  dplyr::summarise(swr_incidence.mean=mean(swr_incidence),
                   swr_incidence.sem=sem(swr_incidence),
                   has_ripples.pct=sum(swr_incidence > 0) / n(),
                   nripples.mean = mean(nripples)) 

xlabels = rep(c('off', 'on'), 2)

swr.baseline.summary %>%
  #dplyr::mutate(date_animal = paste(format(date), animal, sep='_'),
  #              date_laser_val = as.numeric(date) + (as.numeric(laserOn) - 1) * 0.5 - 0.25) %>% 
  ggplot() +
  geom_point(aes(x=laserOn, y=swr_incidence.mean, color=animal)) +
  geom_line(aes(x=laserOn, y=swr_incidence.mean, group=animal)) +
  geom_ribbon(aes(x=laserOn, 
                  ymin=swr_incidence.mean - swr_incidence.sem, 
                  ymax=swr_incidence.mean + swr_incidence.sem,
                  group=animal), 
                alpha=0.1) +
  xlab('Stimulation') + ylab('Ripple incidence (Hz)') +
  facet_grid(. ~ channelLocation) +
  scale_x_discrete(labels=xlabels) +
  scale_y_continuous(breaks=c(0.0, 0.2, 0.4)) +
  gtheme
ggsave(file=paste0(img_dir, '/', '2_sleep_ripples_stats.pdf'), 
       width=5, height=5, unit='cm', dpi=300, device=cairo_pdf)
```

```{r}
psddf %>%
  ggplot(aes(x=laserOn, y=swr_incidence)) +
  geom_boxplot() +
  facet_grid(animal ~ channelLocation) + 
    xlab('Stimulation') + ylab('Ripple incidence (Hz)') +
  scale_x_discrete(labels=xlabels) +
  gtheme
  
```
BD ripples over time
```{r}
psddf %>%
  filter(animal == 'BD') %>%
  ggplot() +
  geom_boxplot(aes(x=trial_id, y=swr_incidence, color=laserOn)) +
  facet_grid(channelLocation ~ .) +
  gtheme
```



