---
title: "Effect of cholinergic stimulation on CA1 and CA3 PSD"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(include=TRUE, collapse=TRUE, warning=FALSE, echo=FALSE)
```

Effects of the laser activation on the signal recorded in baseline conditions.

```{r include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)
library(ggpubr)
select = dplyr::select

source('laser_stats.R')
source('plotting_params.R')
source('psd_analysis.R')
source('psd_fitting.R')
```


```{r include=FALSE}
experiment_name = 'baseline'
img_dir = paste0('/home/prez/tmp/ymaze_chat_x_ai32/img_gen/', experiment_name)
diode.signal = TRUE
data_dir = paste0('/mnt/DATA/chat_ripples/', experiment_name)

if (diode.signal) {
  input.filename = 'welch_psd_table_diode_th7.csv'
} else {
  input.filename = 'welch_psd_table_th7.csv'
}
psddf = bind_rows(
  read_csv(file.path(data_dir, 'trial_results', input.filename)),
  read_csv(file.path(data_dir, 'trial_results_gfp', input.filename)))

psddf = tidyr::replace_na(psddf, list(exp = 'main-effect')) %>%
  dplyr::mutate(exp_animal = paste(exp, animal, sep='_'),
                trial_id=paste(date, animal, trial ,sep='_'))
psddf$exp = as.factor(psddf$exp)
psddf$animal = as.factor(psddf$animal)
psddf$exp_animal = as.factor(psddf$exp_animal)
psddf$channel = as.factor(psddf$channel)
psddf$laserOn = as.factor(psddf$laserOn)
psddf$trial_id = as.factor(psddf$trial_id)
max.noise.dur.sec = 5  # threshold for uninterrupted sleep / lack of noise in the signal
```


Export epochs in succession (for manual count from csv)
```{r}
psddf %>% 
  filter(channelLocation == 'CA1', stage_desc != 'after_stim') %>%
  dplyr::select(exp, animal, noise_dur_sec, trial, trial_id, stage_desc, laserOn) %>%
  filter(noise_dur_sec > max.noise.dur.sec) 
  #write_csv('/tmp/sleep_epochs.csv')

epochs_succession_len = c(80, 20, 30, 7, 19, 16, 5, 5, 12, 19, 5, 4, 11, 8, 12, 50, 14, 4, 17, 14, 12, 3, 1)
summary(epochs_succession_len)
```

```{r}
psddf = psddf %>%
  filter(noise_dur_sec <= max.noise.dur.sec) %>%
  filter(channelLocation == 'CA1')

freq.bands.df = data.frame(
  band=c('theta', 'slow gamma'),
  xmin=c(5, 25),
  xmax=c(12, 45)
)
rownames(freq.bands.df) = freq.bands.df$band
```

Number of trials per animal
```{r}
psddf %>% 
  filter(stage_desc != 'after_stim') %>%
  dplyr::mutate(epoch_id=paste(trial_id, laserOn, sep='_laser')) %>%
  dplyr::summarise(ntrials=length(unique(epoch_id)))
                   
psddf %>% 
  filter(stage_desc != 'after_stim') %>%
  group_by(animal, exp, date) %>%
  dplyr::summarise(ntrials=length(unique(trial_id))) %>%
  group_by(exp) %>%
  dplyr::summarise(mean(ntrials), sem(ntrials), nanimals=n())
```

# Effects on the signal spectrum
```{r}
psd.molten = melt.freq.bands(psddf, extra.id.vars = c('state', 'exp', 'exp_animal'))
```

# PSD diffs on paired trials
```{r}
all.freq.bands.df = data.frame(
  band=c('slow', 'supra_theta', 'supra_slow_gamma'),
  xmin=c(3.5, 12, 90),
  xmax=c(5, 15, 110)
  #xmin=c(3.5, 12, 130),
  #xmax=c(5, 15, 150)
) %>% bind_rows(freq.bands.df) %>%
  dplyr::arrange(xmin)
rownames(all.freq.bands.df) = all.freq.bands.df$band

get.band.name = function(freq) {
  band_ind = which(freq <= all.freq.bands.df$xmax & freq > all.freq.bands.df$xmin)
  if (length(band_ind) > 0) {
    return(as.character(all.freq.bands.df$band[band_ind]))
  } else {
    return('ignored')
  }
}
```


```{r}
psd.diff = reshape2::dcast(psd.molten,
                  animal + date + trial_id + channelLocation + band_name + band_start_freq + state + exp ~ stage_desc,
                  value.var = 'band_power') %>% 
    dplyr::mutate(logpower.diff = log(stim) - log(before_stim))

animal.psd.diff = psd.diff %>%
  dplyr::group_by(band_name, band_start_freq, channelLocation, state, exp, animal) %>%
  dplyr::summarise(logpower.diff.mean=mean(logpower.diff, na.rm=TRUE),
                   logpower.diff.sem=sem(logpower.diff))
  
animal.psd.diff %>%
  filter(channelLocation == 'CA1') %>%
  ggplot() +
  geom_ribbon(aes(x=band_start_freq, group=channelLocation, ymin=logpower.diff.mean-logpower.diff.sem, ymax=logpower.diff.mean+logpower.diff.sem),
              alpha=0.25) +
  geom_line(aes(x=band_start_freq, group=channelLocation, y=logpower.diff.mean, colour=exp), width=0.5) + 
  geom_rect(data=all.freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band, fill=band), 
            ymin=-3, ymax=5, alpha=0.05) +
  scale_x_log10(limits=c(2,200), breaks=axis.breaks, labels=axis.labels) +
  geom_hline(yintercept=0, linetype='dashed') +
  facet_wrap(exp + animal ~ ., ncol = 4, scales = 'free_x') +
  xlab('Frequency (Hz)') +
  ylab('Log power change') +
  scale_color_manual(values=expPalette) +
  theme(legend.position = 'right') +
  gtheme

ggsave(file=paste0(img_dir, '/', '2_psd_change_all.pdf'), 
       width=23, height=17, unit='cm', dpi=300, device=cairo_pdf)
```

Minimum and maximum difference per freq band
```{r warning=FALSE}
band.logpower.diff = psd.diff %>%
  dplyr::mutate(band_name = map_chr(band_start_freq, get.band.name)) %>% 
  group_by(exp, animal, date, channelLocation, state, trial_id, band_name) %>%
  dplyr::summarise(min.band.logpower.diff = min(logpower.diff, na.rm=TRUE),
                   max.band.logpower.diff = max(logpower.diff, na.rm=TRUE)) %>%
  filter(!is.infinite(min.band.logpower.diff), !is.infinite(max.band.logpower.diff)) %>% # skip trials when NA for logpower.diff
  dplyr::mutate(exp_animal = paste(exp, animal, sep='_'))

band.logpower.diff$band_name = factor(band.logpower.diff$band_name, levels=c(as.character(all.freq.bands.df$band), 'ignored'))
```

```{r}
band.relative.diff = band.logpower.diff %>%
  dplyr::mutate(band.logpower.diff = max.band.logpower.diff) %>%
                  #ifelse(band_name %in% c('theta', 'slow_gamma'), max.band.logpower.diff, min.band.logpower.diff)) %>% 
  reshape2::dcast(
   animal + date + trial_id + channelLocation + exp + exp_animal ~ band_name,
   value.var = 'band.logpower.diff') %>% 
   dplyr::mutate(theta_above_slow = theta - slow, 
                 theta_above_supra = theta - supra_theta,
                 slow_gamma_above_supra_theta = `slow gamma` - supra_theta,
                 slow_gamma_above_supra = `slow gamma` - supra_slow_gamma) %>% 
  dplyr::select(-c(theta, slow, supra_theta, `slow gamma`, supra_slow_gamma, ignored)) %>%
  reshape2::melt(id.vars = c('animal', 'date', 'trial_id', 'channelLocation', 'exp', 'exp_animal'), 
                 variable.name='compared.bands',
                 value.name='relative.diff') 

band.relative.diff %>%
  filter(channelLocation == 'CA1') %>%
  ggplot(aes(x=exp, y=relative.diff)) +
  geom_jitter(aes(color=exp), shape=1, width=0.25, height=0, alpha=0.5, size=0.5, stroke=0.5) +
  geom_hline(yintercept=0, linetype='dashed') +
  facet_wrap(compared.bands ~ ., ncol=4) +
  scale_color_manual(values=expPalette) +
  ylim(c(-0.8, 1.6)) +
  gtheme +
  xlab('') + ylab('Relative difference in change')
ggsave(file=paste0(img_dir, '/', '2_psd_diff_stat.pdf'), 
       width=10, height=5.5, unit='cm', dpi=300, device=cairo_pdf)

```


```{r}
tested.df = filter(band.relative.diff, channelLocation == 'CA1', 
                                    #compared.bands == 'theta_above_slow')
                                    compared.bands == 'theta_above_supra')
                                    #compared.bands == 'slow_gamma_above_supra')
                                    #compared.bands == 'slow_gamma_above_supra_theta')
m.full = lmerTest::lmer(relative.diff ~ exp + (1 + exp | exp_animal), 
                        data=tested.df,
                        REML = TRUE) 
summary(m.full)
anova(m.full, refit=FALSE, ddf='Satterthwaite')
plot.model.diagnostics(m.full, tested.df$animal, tested.df$exp)
```

Trial PSD diff
```{r}
psd.diff %>%
  filter(trial_id == '2020-08-12_TL_TL_sleep_5_g0_0', channelLocation == 'CA1', band_start_freq >= 2) %>%
  ggplot(aes(x=band_start_freq, y=logpower.diff)) +
  geom_line() +
  #geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
  #    ymin=-1, ymax=5, alpha=0.05, fill='grey10') +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  #geom_hline(yintercept=0, linetype='dashed') +
  facet_wrap(exp ~ .) +
  xlab('Frequency (Hz)') +
  ylab('LFP power ratio') +
  gtheme
```


# PSD and background spectrum fit
```{r include = FALSE}
animals.psd = psd.molten %>%
  filter(stage_desc %in% c('stim', 'before_stim')) %>%
  group_by(channelLocation, animal, exp, exp_animal, laserOn, stage_desc, band_start_freq) %>%
  dplyr::summarise(sem.power = sem(log(band_power)), 
                   band_power = mean(log(band_power)))

exp.animals.df = dplyr::select(ungroup(animals.psd), exp, animal) %>% dplyr::distinct()
joined.psd.fit.df = map_dfr(1:nrow(exp.animals.df), ~ {
  animal_name = exp.animals.df$animal[.x]
  exp_name = exp.animals.df$exp[.x]
  animal.psd = filter(animals.psd, animal == animal_name, exp == exp_name)
  animal.psd$name = 'model'
  animal.fit.low.freq = calc.animal.band.fit.df(animal.psd, c(3, 15)) %>%
  #animal.fit.low.freq = calc.animal.band.fit.df(animal.psd, c(3.5, 150), fit.knee = TRUE) %>%
    dplyr::mutate(animal = animal_name, exp = exp_name, name = paste(name, 'low_freq', sep='_'))
  animal.fit.high.freq = calc.animal.band.fit.df(animal.psd, c(15, 150)) %>%
  #animal.fit.high.freq = calc.animal.band.fit.df(animal.psd, c(3.5, 150), fit.knee = TRUE) %>%
    dplyr::mutate(animal = animal_name, exp = exp_name, name = paste(name, 'high_freq', sep='_'))
  bind_rows(animal.psd, animal.fit.low.freq, animal.fit.high.freq)
})
```

```{r}
ca1.psd.fit.df = filter(joined.psd.fit.df, channelLocation != 'CA3') %>%
  dplyr::mutate(name_laser=paste(name, laserOn, sep='_'))
ca1.psd.fit.df %>%
  ggplot() +
  geom_ribbon(aes(x=band_start_freq, y=band_power, 
              group=name_laser, fill=laserOn,
              ymin=band_power - sem.power, ymax=band_power + sem.power), 
          alpha=0.8) +
  geom_line(data=filter(ca1.psd.fit.df, name != 'model'),
            aes(x=band_start_freq, y=band_power, 
                group=name_laser, color=laserOn, linetype=name), size=0.5) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-20, ymax=-5, alpha=0.05, fill='grey10') +
  facet_wrap(exp + animal ~ channelLocation, scales = 'free', ncol = 4) +
  scale_x_log10(limits=c(2,200), breaks=axis.breaks, labels=axis.labels) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  #ylim(-18.3,-7.2) +
  #scale_y_continuous(breaks=c(-15,-10))+
  gtheme +
  theme(legend.position = 'right') +
  scale_linetype_manual(values=c('dotted', 'dotted', 'solid')) +
  xlab('Frequency (Hz)') + ylab('Log power')

#ggsave(file=paste0(img_dir, '/', '2_psd_mean.pdf'), 
#       width=13.5, height=6.5, unit='cm', dpi=300, device=cairo_pdf)
 
ggsave(file=paste0(img_dir, '/', '2_psd_mean_all.pdf'), 
       width=20, height=17, unit='cm', dpi=300, device=cairo_pdf)
```


```{r}
plotted.lowfreq.fit = joined.psd.fit.df
bind_rows(animals.psd, plotted.lowfreq.fit) %>%
  filter(channelLocation == 'CA1') %>%
  filter(animal == 'BS', exp == 'main-effect') %>%
  dplyr::mutate(name_laser=paste(name, laserOn, sep='_')) %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, y=band_power, 
                group=name_laser, color=laserOn, linetype=name)) +
  geom_ribbon(aes(x=band_start_freq, y=band_power, 
                  group=name_laser, fill=laserOn,
                  ymin=band_power - sem.power, ymax=band_power + sem.power), 
              alpha=0.2) +
  scale_x_log10(limits=c(2,150), breaks=axis.breaks, labels=axis.labels) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  scale_linetype_manual(values=c('dashed', 'dashed', 'solid')) +
  facet_grid(. ~ channelLocation, scales = 'free') +
  gtheme +
  theme(legend.position = 'none') +
  xlab('Frequency (Hz)') + ylab('Log power')
ggsave(file=paste0(img_dir, '/', '2_psd_fit_inset.pdf'), 
       width=8, height=8, unit='cm', dpi=300, device=cairo_pdf)
```


```{r}
trial.molten.psd = psd.molten %>%
  filter(animal == 'TL', exp == 'main-effect') %>%
  dplyr::mutate(trial_id_laser = paste(trial_id, laserOn, sep='_'))

library(permute)
sample.n.trials = function(df, n=5) {
   trial.ids = unique(df$trial_id)
   #set.seed(42)
   trial.ids = trial.ids[permute::shuffle(length(trial.ids))]
   n = min(n, length(trial.ids))
   trial.ids = trial.ids[1:n]
   filter(df, trial_id %in% trial.ids)
}

bind_rows(
  sample.n.trials(filter(trial.molten.psd, stage_desc == 'before_stim'), n=5),
  sample.n.trials(filter(trial.molten.psd, stage_desc == 'stim'), n=5)
) %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, y=log(band_power), group=trial_id_laser, color=laserOn), size=0.5*px2pt) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-25, ymax=-5, alpha=0.05, fill='grey10') +
  facet_grid(animal ~ channelLocation, scales = 'free') +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  #xlim(c(3,80)) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  gtheme +
  xlab('Frequency (Hz)') + ylab('Power (log)')

ggsave(file=paste0(img_dir, '/', '2_psd_indiv_traces.pdf'), 
       width=12.5, height=6, unit='cm', dpi=300, device=cairo_pdf)
```


# PSD fit

```{r}
fit.psd.df.all = fit.background.df(filter(psd.molten, stage_desc != 'after_stim'), 
                               freq.bands.df, c(3.5, 150), 
                               fit.knee = TRUE, 
                               extra.group.vars = c('exp_animal'))

summary(fit.psd.df.all$fit_error)
summary(fit.psd.df.all$r_squared)
```

Fit background with FOOOF and check quality
```{r}
fit.psd.df.high = fit.background.df(filter(psd.molten, stage_desc != 'after_stim'), 
                               freq.bands.df, c(15, 150), 
                               fit.knee = FALSE, 
                               extra.group.vars = c('exp_animal'))

summary(fit.psd.df.high$fit_error)
summary(fit.psd.df.high$r_squared)
fit.psd.df.high$correct = 1
```


Aperiodicity reduced:
Background offset reduced, but slope also increased -> PSD starts lower but decreases less with freq,
```{r}
g.bac.auc = plot.samples(filter(fit.psd.df.high, channelLocation == 'CA1'), background_auc) + ylab('Background spectrum AUC')
g.bac.auc
m.full = calc.laser.fixed.effects(filter(fit.psd.df.high, channelLocation == 'CA1'), background_auc)
pairwise.post.hoc(m.full) 
print('ntrials: ')
length(unique(fit.psd.df.high$trial_id))
```
```{r}
fit.psd.df.high %>% 
  group_by(exp, channelLocation, laserOn) %>%
  dplyr::summarise(mean(background_auc, na.rm=T), sem(background_auc))
```

## Slow Gamma
Count of trials with slow gamma:
```{r}
var = quo(pow_slow_gamma)
pct.theta.oscillating = group_by(fit.psd.df.high, channelLocation, exp, animal, laserOn) %>%
  dplyr::summarise(pct.oscillating=sum(!is.na(!!var)) / n())
pct.theta.oscillating
ca.subset = subset(pct.theta.oscillating, channelLocation == 'CA1' & exp == 'main-effect')
t.test(subset(ca.subset, laserOn==0 & exp == 'main-effect')$pct.oscillating,
       subset(ca.subset, laserOn==1 & exp == 'main-effect')$pct.oscillating, 
       paired=TRUE)
group_by(pct.theta.oscillating, exp, channelLocation, laserOn) %>%
  dplyr::summarise(mean(pct.oscillating), sem(pct.oscillating))
```

Significant increase in slow gamma:
```{r}
var = quo(pow_slow_gamma)
fit.sgamma.present = fit.psd.df.high %>%
  filter(!is.na(!!var))
  #dplyr::mutate(!!var := ifelse(is.na(!!var), 0, !!var))

g.sgamma.pow = plot.samples(filter(fit.sgamma.present, channelLocation == 'CA1'), !!var) + 
  ylab('Relative Slow Gamma Power (25 - 45 Hz)')
g.sgamma.pow
m.full = calc.laser.fixed.effects(subset(fit.sgamma.present, channelLocation == 'CA1'), log(!!var))
pairwise.post.hoc(m.full)
length(unique(fit.sgamma.present$trial_id))

fit.sgamma.present %>% group_by(channelLocation, laserOn) %>% dplyr::summarise(mean(!!var, na.rm=T), sem(!!var))
```


SGamma central frequency when the laser on
```{r}
peak_var = quo(peak_slow_gamma)

filter(fit.psd.df.high, !is.na(!!peak_var)) %>%
  group_by(animal, channelLocation, exp, laserOn) %>% 
  dplyr::summarise(peak.mean = mean(!!peak_var),
                   peak.median = median(!!peak_var),
                   peak.sem = sem(!!peak_var)) %>% 
  dplyr::group_by(channelLocation, exp, laserOn) %>%
  dplyr::summarise(mean(peak.mean), sem(peak.mean))

plot.laser.change(fit.psd.df.high, !!peak_var) + ylab('Central Slow Gamma frequency (Hz)')
calc.laser.fixed.effects(filter(fit.sgamma.present, channelLocation == 'CA1', !is.na(!!peak_var)), !!peak_var)
#calc.laser.fixed.effects(filter(fit.sgamma.present, channelLocation == 'CA3', !is.na(!!peak_var)), !!peak_var)
```


## Theta
Fit background with FOOOF and check quality
```{r}
fit.psd.df.low = fit.background.df(filter(psd.molten, stage_desc != 'after_stim'), 
                               freq.bands.df,
                               c(3.5, 15),
                               fit.knee = FALSE,
                               extra.group.vars = c('exp_animal'))

summary(fit.psd.df.low$fit_error)
summary(fit.psd.df.low$r_squared)
fit.psd.df.low$correct = 1
```

Count of trials with theta:
```{r}
var = quo(pow_theta)
pct.theta.oscillating = group_by(fit.psd.df.low, channelLocation, exp, animal, laserOn) %>%
  dplyr::summarise(pct.oscillating=sum(!is.na(!!var)) / n())
pct.theta.oscillating
ca.subset = subset(pct.theta.oscillating, channelLocation == 'CA1')
t.test(subset(ca.subset, laserOn==0 & exp == 'main-effect')$pct.oscillating,
       subset(ca.subset, laserOn==1 & exp == 'main-effect')$pct.oscillating, 
       paired=TRUE)
group_by(pct.theta.oscillating, exp, channelLocation, laserOn) %>% dplyr::summarise(mean(pct.oscillating), sem(pct.oscillating))
```

Significant increase in theta power
```{r}
var = quo(pow_theta)
fit.theta.present = fit.psd.df.low %>%
  filter(!is.na(!!var))

m.full = calc.laser.fixed.effects(filter(fit.theta.present, channelLocation == 'CA1'), 
                                  log(pow_theta))
pairwise.post.hoc(m.full)
g.theta.pow = plot.samples(filter(fit.theta.present, channelLocation == 'CA1'), pow_theta) + ylab('Relative theta power (5 - 12 Hz)')
g.theta.pow
fit.psd.df.low %>% group_by(channelLocation, exp, laserOn) %>% dplyr::summarise(mean(!!var, na.rm=T), sem(!!var))
```

Lower theta central frequency when the laser on
```{r}
peak_var = quo(peak_theta)
filter(fit.psd.df.low, !is.na(!!peak_var)) %>%
  group_by(animal, channelLocation, laserOn) %>%
  dplyr::summarise(peak_theta.mean = mean(!!peak_var),
                   peak_theta.median = median(!!peak_var),
                   peak_theta.sem = sem(!!peak_var)) %>%
  dplyr::group_by(channelLocation, laserOn) %>%
  dplyr::summarise(mean(peak_theta.mean), sem(peak_theta.mean))

g.theta.freq = plot.samples(filter(fit.psd.df.low, channelLocation == 'CA1'), !!peak_var) + ylab('Theta peak frequency (Hz)')
g.theta.freq
m.full = calc.laser.fixed.effects( filter(fit.psd.df.low, !is.na(!!peak_var), channelLocation == 'CA1'), log(!!peak_var))
pairwise.post.hoc(m.full)
#calc.laser.fixed.effects( filter(fit.psd.df.low, !is.na(!!peak_var), channelLocation == 'CA3'), !!peak_var)
```

```{r}
plot_grid(g.bac.auc, g.theta.pow, g.theta.freq, g.sgamma.pow, ncol=4)
ggsave(file=paste0(img_dir, '/', '2_psd_stats.pdf'), 
       width=14, height=5.0, unit='cm', dpi=300, device=cairo_pdf)
```

