---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r include=FALSE}
knitr::opts_chunk$set(include=TRUE, collapse=TRUE, warning=FALSE, echo=FALSE)
```

```{r include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)
library(ggpubr)
library(purrr)
select = dplyr::select

source('laser_stats.R')
source('plotting_params.R')
source('psd_analysis.R')
source('psd_fitting.R')
```


```{r read_data,  include=FALSE}
diode.signal = TRUE

img_dir = '/home/prez/tmp/ymaze_chat_x_ai32/img_gen/ymaze'
data_dir = '/mnt/DATA/chat_ripples/y-maze'

if (diode.signal) {
  ripples.inputfilename = 'ripples_diode_th7.csv'
  input.filename = 'welch_psd_table_diode_th7.csv'
} else {
  ripples.inputfilename = 'ripples_th7.csv'
  input.filename = 'welch_psd_table_th7.csv'
}
psddf.ymaze = bind_rows(
  read_csv(file.path(data_dir, 'trial_results', input.filename)),
  read_csv(file.path(data_dir, 'trial_results_gfp', input.filename)))
ripples.ymaze = bind_rows(
  read_csv(file.path(data_dir, 'trial_results', ripples.inputfilename)),
  read_csv(file.path(data_dir, 'trial_results_gfp', ripples.inputfilename)))

psddf.ymaze = prepare.ymaze.df(psddf.ymaze) %>%
  dplyr::mutate(exp_animal = paste(exp, animal, sep='_')) 
ripples.ymaze = prepare.ymaze.df(ripples.ymaze) %>%
  dplyr::mutate(exp_animal = paste(exp, animal, sep='_')) 
```


Join trial metadata (includes if the mouse made correct choice)
```{r}
trials.info.filename = 'trials.csv'
trial.info.df = read_csv(file.path(data_dir, trials.info.filename)) %>%
  dplyr::mutate(file_name=paste0('signal/', animal, '_trial_', trial, '_g0'))
trial.info.df$date = as.Date(trial.info.df$date, '%d/%m/%Y')
```

```{r}
psddf.ymaze = left_join(psddf.ymaze, dplyr::select(trial.info.df, -trial, -state, -laserOn), 
                        by=c('date', 'animal', 'file_name', 'exp'))
ripples.ymaze = left_join(ripples.ymaze, dplyr::select(trial.info.df, -trial, -state, -laserOn), 
                        by=c('date', 'animal', 'file_name', 'exp'))

psddf.ymaze$channelLocation = as.factor(psddf.ymaze$channelLocation)
psddf.ymaze$exp = as.factor(psddf.ymaze$exp)
psddf.ymaze$exp_animal = as.factor(psddf.ymaze$exp_animal)
psddf.ymaze$animal = as.factor(psddf.ymaze$animal)
```

Performance reached 80 % 
```{r}
psddf.ymaze %>%
  filter(stage_desc == 'Total', channelLocation == 'CA1') %>%
  group_by(exp, animal, learning_day) %>%
  dplyr::summarise(pct.correct=mean(correct), ncorrect=sum(correct)) %>% 
  group_by(learning_day) %>%
  dplyr::summarise(mean(pct.correct),
                   sem(pct.correct), 
                   mean(ncorrect),
                   mean(pct.correct >= 0.80),
                   n())
```
Duration spend in goal zone in correct vs incorrect trials
```{r}
stage.dur.df = psddf.ymaze %>% 
  filter(exp == 'main-effect', channelLocation == 'CA1') %>%
  filter(stage_dur_sec > 0) %>% # ignore trials with failed tracking
  filter(stage_desc %in% c('DuringStim'))

stage.dur.df$correct = as.logical(stage.dur.df$correct)
stage.dur.df %>%
  ggplot(aes(x=correct, y=stage_dur_sec)) +
  geom_boxplot() +
  gtheme + 
  xlab('Trial correct') + ylab('Duration (s)')

stage.dur.df %>%
  dplyr::mutate(lfp_signal_sec=stage_dur_sec - noise_dur_sec) %>%
  group_by(correct) %>%
  dplyr::summarise(mean(stage_dur_sec), sem(stage_dur_sec), mean(lfp_signal_sec), sem(lfp_signal_sec), n())
```


Duration spend during navigation vs goal zone 
```{r}

goal.loc.durs = psddf.ymaze %>% 
  filter(channelLocation == 'CA1') %>%
  filter(correct == 1) %>%
  filter(stage_dur_sec > 0) %>% # ignore trials with failed tracking
  filter(stage_desc == 'DuringStim')
m.full = calc.laser.fixed.effects(goal.loc.durs, stage_dur_sec)

stage.dur.df = psddf.ymaze %>% 
  filter(exp == 'main-effect', channelLocation == 'CA1') %>%
  filter(correct == 1) %>%
  filter(stage_dur_sec > 0) %>% # ignore trials with failed tracking
  filter(stage_desc %in% c('BeforeGoalZone', 'DuringStim'))

stage.dur.df %>%
  filter(learning_day <= 2) %>%
  ggplot(aes(x=stage_desc, y=stage_dur_sec)) +
  geom_boxplot() +
  gtheme +
  xlab('') + ylab('Duration (s)') +
  scale_x_discrete(labels=c('Stimulation during navigation', 'Stimulation at goal'))

stage.dur.df %>%
  group_by(date, learning_day, correct, laserOn, stage_desc) %>% 
  dplyr::summarise(mean(stage_dur_sec), sem(stage_dur_sec), min(stage_dur_sec), max(stage_dur_sec), n=n()) 

stage.dur.df %>%
  dplyr::ungroup() %>%
  filter(correct==1) %>%
  group_by(stage_desc, laserOn) -> X
dplyr::summarise(X, mean(stage_dur_sec), sem(stage_dur_sec), max(stage_dur_sec))


quantile(X$stage_dur_sec, probs = c(0.05, 0.95))
```



Ripples incidence at Goal in correct trials per animal 
```{r}
min.stim.stage.dur.sec = 10
psddf.ymaze.correct = filter(psddf.ymaze, correct == 1)

nripples.summary = psddf.ymaze.correct %>%
  filter(laserOn == 0, learning_day >= 1, stage_desc == 'DuringStim', channelLocation == 'CA1') %>%
  filter(stage_dur_sec - noise_dur_sec >= min.stim.stage.dur.sec) %>%
  group_by(exp, animal, exp_animal) %>%
  dplyr::summarise(has_ripples.pct=sum(swr_incidence > 0) / n(),
                   mean.incidence = mean(swr_incidence),
                   mean.ripple.incidence = mean(ripple_incidence),
                   n=n()) 
nripples.summary

excluded.swr.exp_animals = subset(nripples.summary, mean.incidence < 0.01)$exp_animal
```


Ripples at correct vs incorrect trials at Goal
```{r}
compared.ripples.df = psddf.ymaze %>%
  filter(stage_desc %in% c('DuringStim', 'StartZone'), 
         channelLocation == 'CA1') %>%
  filter(!(exp_animal %in% excluded.swr.exp_animals)) 

compared.ripples.df %>%
  filter(stage_desc == 'DuringStim') %>%
  group_by(correct, laserOn) %>%
  dplyr::summarise(n())

compared.ripples.df %>%
  filter(stage_desc == 'DuringStim') %>%
  group_by(exp, correct, laserOn) %>%
  dplyr::summarise(has_ripples.pct=mean(has_ripples),
                   mean.incidence = mean(swr_incidence),
                   sem.incidence = sem(swr_incidence),
                   n=n()) 
```
Comparison of ripples at goal between correct and incorrect trials
```{r}
compared.ripples.df$correct = as.factor(compared.ripples.df$correct)
compared.ripples.df$stage_desc = as.factor(compared.ripples.df$stage_desc)
compared.ripples.df$exp_animal = as.factor(compared.ripples.df$exp_animal)
compared.ripples.df$correct = as.factor(compared.ripples.df$correct)

animal.summary.ripples = compared.ripples.df %>%
  filter(stage_desc == 'StartZone' | laserOn == 0) %>%
  filter(!is.na(correct)) %>%
  group_by(exp_animal, exp, animal, stage_desc, correct) %>%
  dplyr::summarise(has_ripples.pct=mean(has_ripples),
                   has_swrs.pct=mean(swr_incidence > 0),
                   mean.nripples=mean(nripples),
                   mean.incidence = mean(swr_incidence), n=n()) 

animal.summary.ripples.goal = filter(animal.summary.ripples, stage_desc == 'DuringStim') 
t.test(subset(animal.summary.ripples.goal, correct==0)$has_swrs.pct,
       subset(animal.summary.ripples.goal, correct==1)$has_swrs.pct,
       paired=TRUE)
```

Summary of ripples per animal and day
```{r}
psddf.ymaze.correct %>%
  filter(stage_desc == 'Total', channelLocation == 'CA1') %>%
  filter(!(exp_animal %in% excluded.swr.exp_animals)) %>%
  group_by(laserOn) %>%
  dplyr::summarise(n=n())

psddf.ymaze.correct %>%
  filter(!(exp_animal %in% excluded.swr.exp_animals)) %>%
  filter(laserOn == 0, learning_day >= 1, stage_desc == 'Total', channelLocation == 'CA1', exp == 'main-effect') %>%
  group_by(exp, animal, learning_day) %>%
  dplyr::summarise(has_ripples.pct=sum(swr_incidence > 0) / n(),
                   mean.incidence = mean(swr_incidence)) 
```


Plot ripples over trial
```{r}
selected.stages = c('StartZone', 'DuringStim')
trials.sample = psddf.ymaze.correct %>%
  filter(learning_day == 6, animal == 'PT') %>%
  #filter(learning_day == 4, animal=='BR') %>%
  filter(stage_desc %in% selected.stages)

trial.renumber = trials.sample %>% 
  dplyr::select(laserOn, channelLocation, trial_no) %>% 
  dplyr::group_by(laserOn, channelLocation) %>%
  dplyr::distinct() %>%
  dplyr::arrange(trial_no) %>%
  dplyr::mutate(trial_rank = row_number(trial_no))

ripples.sample = ripples.ymaze %>% 
  filter(stage_desc %in% selected.stages)  %>%
  filter(trial_id %in% trials.sample$trial_id) 

trials.sample = left_join(trials.sample, trial.renumber)
ripples.sample = left_join(ripples.sample, trial.renumber)

 ggplot() +
  geom_tile(data=trials.sample, aes(x=stage_dur_sec/2, y=trial_rank, width=stage_dur_sec), fill='grey90', colour='grey50') +
  geom_tile(data=ripples.sample, aes(x=peak_t, y=trial_rank, fill=laserOn), width=0.5) +
  facet_grid(channelLocation + laserOn ~ stage_desc) +
  scale_fill_manual(labels=c('Off', 'On'), values=c(nolaser.col, laser.col)) +
  gtheme +
  scale_y_continuous(breaks=c(2,4), trans='reverse') +
  xlab('Time (s)') + ylab('Trial number')

  ggsave(paste0(img_dir, '/indiv_ripples_time.pdf'), units = 'cm',
       dpi=300, device=cairo_pdf,
       height=6, width=12)
```

Ripple incidence over learning
```{r}
psddf.ymaze.correct %>%
  filter(stage_desc == 'DuringStim') %>%
  ggplot() +
  geom_jitter(aes(x=learning_day, y=ripple_incidence, color=laserOn), width=0.3) +
  facet_grid(exp + animal ~ channelLocation, scales='free')
```


Signif testing including gfp-control
```{r}
ca1.psddf = filter(psddf.ymaze.correct, channelLocation == 'CA1', stage_desc == 'DuringStim') %>%
  mutate(exp_animal = paste(exp, animal, sep='_')) %>%
  filter(!(exp_animal %in% excluded.swr.exp_animals)) %>%
  dplyr::select(-starts_with('all_psd'))
ca1.psddf$correct = as.factor(ca1.psddf$correct)
m.full = calc.laser.fixed.effects(ca1.psddf, log(0.1+swr_incidence))

pairwise.post.hoc(m.full) 
```

Difference in ripples over the duration of learning
```{r}
m.full = ca1.psddf %>%
  mutate(early.learning = learning_day < 5) %>%
  filter(laserOn == 0, stage_desc == 'DuringStim') %>%
  calc.laser.fixed.effects(swr_incidence, 
                           fixed.effects.str = 'early.learning',
                           random.effects.str = '(1 | exp_animal)')

ca1.psddf %>%
  filter(laserOn == 0, stage_desc == 'DuringStim') %>%
  ggplot(aes(x=learning_day, y=swr_incidence)) +
  geom_jitter(aes(color=exp), shape=1, width=0.25, height=0, alpha=0.5, size=0.5, stroke=0.5) +
  scale_color_manual(values=expPalette) +
  xlab('Learning day') + ylab('SWR incidence (Hz)') +
  gtheme + theme(legend.position = 'none')

ggsave(file.path(img_dir, '5-ripples_over_learning.pdf'), units = 'cm',
       dpi=300, device=cairo_pdf,
       height=3.7, width=4)
```


```{r}
plot.samples(ca1.psddf, swr_incidence) +
  #ylim(c(0, 0.35)) +
  ylab('SWR incidence (Hz)')

ggsave(paste0(img_dir, '/5-ripples_incidence.pdf'), units = 'cm',
       dpi=300, device=cairo_pdf,
       height=5, width=4)
```

# CA1 ripple params

Peak frequency
```{r}
ca1.ripple.df = filter(ripples.ymaze, channelLocation == 'CA1', stage_desc == 'DuringStim') %>%
  dplyr::mutate(ripple_dur = end_time - start_sec)

ripple_freqs = pull(filter(ca1.ripple.df, laserOn==0, peak_freq >= 140), peak_freq)
summary(ripple_freqs)
sem(ripple_freqs)
```
Diffference in ripples on correct and incorrect trials
```{r}
tested.df = filter(ca1.ripple.df, laserOn==0, !is.na(correct), peak_freq >= 140)
var = quo(peak_freq)
m.full = calc.laser.fixed.effects(tested.df, 
                                  peak_freq,
                                  fixed.effects.str = 'correct',
                                  random.effects.str = '(1 | animal)')
tested.df %>%
  group_by(correct) %>%
  dplyr::summarise(mean(!!var), sem(!!var), n())


var = quo(ripple_dur)
m.full = calc.laser.fixed.effects(tested.df, 
                                  log10(ripple_dur ^ (-1.5)),
                                  fixed.effects.str = 'correct',
                                  random.effects.str = '(1 | animal)')
tested.df %>%
  group_by(correct) %>%
  dplyr::summarise(mean(!!var) * 1000, sem(!!var) * 1000, n())
```


```{r}
m.full = calc.laser.fixed.effects(filter(ca1.ripple.df, peak_freq >= 140, correct==1), peak_freq^(-1.0))

ggplot(filter(ca1.ripple.df, !is.na(correct), correct == 1), aes(x=peak_freq)) +
  geom_histogram(aes(color=laserOn, y=..count.., fill=laserOn), 
                 breaks=seq(80,250,10), alpha=0.5, position='identity') +
  facet_grid(. ~ exp) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  gtheme +
  xlab('Peak frequency (Hz)') + ylab('# Ripples')

ggsave(file=file.path(img_dir, '5_ripple_peak_freq.pdf'), 
       width=9, height=5.5, unit='cm', dpi=300, device=cairo_pdf)
```

Ripple durations
```{r}
ripple_durs = pull(filter(ca1.ripple.df, laserOn==0, peak_freq >= 140), ripple_dur)
summary(ripple_durs)
sem(ripple_durs)
m.full = calc.laser.fixed.effects(filter(ca1.ripple.df, peak_freq >= 140), log(ripple_dur))

ggplot(filter(ca1.ripple.df, peak_freq >= 140), aes(x=ripple_dur*1000)) +
  geom_histogram(aes(color=laserOn, y=..count.., fill=laserOn), 
                 breaks=seq(20,100,10), alpha=0.5, 
                 position='identity') +
  facet_grid(. ~ exp) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  gtheme +
  xlab('Ripple duration (ms)') + ylab('# SWRs')

ggsave(file=file.path(img_dir, '5_ripple_duration.pdf'), 
       width=9, height=5.5, unit='cm', dpi=300, device=cairo_pdf)
```
    
    
```{r}
ca1.ripple.df %>%
  filter(channelLocation == 'CA1') %>%
  ggplot() +
  geom_histogram(aes(x=peak_freq, fill=animal, color=animal),  position='identity',alpha=0.2) + 
  facet_grid(exp + animal ~ laserOn, scales =  'free_y')
```
    
    