---
title: "R Notebook"
output: html_notebook
---
```{r}
library(purrr)

laser.col='#0098ffff'
nolaser.col='grey30'
```


```{r read_data}
diode.signal = TRUE

data_dir = '/mnt/DATA/chat_ripples/y-maze/'
img_dir = '/home/prez/tmp/ymaze_chat_x_ai32/img_gen/ymaze'

if (diode.signal) {
  psddf.ymaze = read_csv(paste(data_dir, 'trial_results', 'welch_psd_table_diode_th6.csv', sep='/'))
  ripples.ymaze = read_csv(paste(data_dir, 'trial_results', 'ripples_diode_th6.csv', sep='/'))
} else {
  psddf.ymaze = read_csv(paste(data_dir, 'trial_results', 'welch_psd_table_th6.csv', sep='/'))
  ripples.ymaze = read_csv(paste(data_dir, 'trial_results', 'ripples_th6.csv', sep='/'))
}

psddf.ymaze = prepare.ymaze.df(psddf.ymaze)
ripples.ymaze = prepare.ymaze.df(ripples.ymaze)


```


Join trial metadata (includes if the mouse made correct choice)
```{r}
trial.info.df = read_csv(paste(data_dir, 'trials.csv', sep='/')) %>%
  dplyr::mutate(file_name=paste0('signal/', animal, '_trial_', trial, '_g0'))
trial.info.df$date = as.Date(trial.info.df$date, '%d/%m/%Y')
glimpse(trial.info.df)
```

```{r}
library(stringr)
#trial.info.df = dplyr::mutate(trial.info.df, file_name = stringr::str_replace(file_name, '_trial_', '_after_'))
psddf.ymaze = left_join(psddf.ymaze, dplyr::select(trial.info.df, -trial, -state, -laserOn), 
                        by=c('date', 'animal', 'file_name'))
ripples.ymaze = left_join(ripples.ymaze, dplyr::select(trial.info.df, -trial, -state, -laserOn), 
                        by=c('date', 'animal', 'file_name'))
```

Performance reached 70 % 
```{r}
 psddf.ymaze %>%
  group_by(animal, learning_day) %>%
  dplyr::summarise(pct.correct=mean(correct)) %>% 
  group_by(learning_day) %>%
  dplyr::summarise(mean(pct.correct),
                   sem(pct.correct))
```

```{r}
psddf.ymaze.correct = filter(psddf.ymaze, correct == 1)
```

```{r}
psddf.ymaze.correct %>%
  filter(laserOn == 0, learning_day >= 1, stage_desc == 'Total', channelLocation == 'CA1') %>%
  group_by(animal, learning_day) %>%
  dplyr::summarise(has_ripples.pct=sum(swr_incidence > 0) / n(),
                   mean.incidence = mean(swr_incidence)) 
```


Filter animals with few ripples (swr incidence < 0.02)
```{r}
nripples.summary = psddf.ymaze.correct %>%
  filter(laserOn == 0, learning_day >= 1, stage_desc == 'Total', channelLocation == 'CA1') %>%
  group_by(animal) %>%
  dplyr::summarise(has_ripples.pct=sum(swr_incidence > 0) / n(),
                   mean.incidence = mean(swr_incidence)) 
psddf.ymaze.correct = filter(psddf.ymaze.correct, 
                             animal %in% subset(nripples.summary, mean.incidence >= 0.03)$animal)
```

Plot ripples over trial
```{r}
selected.stages = c('StartZone', 'DuringStim')
ripples.sample = ripples.ymaze %>% 
  filter(correct == 1) %>% 
  filter(learning_day == 6, animal=='PT') %>%
  filter(stage_desc %in% selected.stages)

ripples.sample$stage_desc = factor(ripples.sample$stage_desc, 
                                   levels=selected.stages, 
                                   labels=c('Start', 'Goal'),
                                   ordered=TRUE)

trial.renumber = ripples.sample %>% 
  dplyr::select(laserOn, channelLocation, trial_no) %>% 
  dplyr::group_by(laserOn, channelLocation) %>%
  dplyr::distinct() %>%
  dplyr::arrange(trial_no) %>%
  dplyr::mutate(trial_rank = row_number(trial_no))
  
ripples.sample = left_join(ripples.sample, trial.renumber)

ripples.sample %>%
  ggplot() +
  geom_tile(aes(x=peak_t, y=trial_rank, fill=laserOn), width=0.5) +
  facet_grid(channelLocation + laserOn ~ stage_desc) +
  scale_fill_manual(labels=c('Off', 'On'), values=c(nolaser.col, laser.col)) +
  gtheme +
  scale_y_continuous(breaks=c(2,4))+
  xlab('Time (s)') + ylab('Trial number')

  ggsave(paste0(img_dir, '/indiv_ripples_time.pdf'), units = 'cm',
       dpi=300, device=cairo_pdf,
       height=6, width=12)
```

Ripple incidence over learning
```{r}
psddf.ymaze.correct %>%
  filter(stage_desc == 'DuringStim') %>%
  ggplot() +
  geom_jitter(aes(x=learning_day, y=swr_incidence, color=laserOn), width=0.2) +
  facet_grid(animal ~ channelLocation, scales='free')
```


```{r}
swr.ymaze.summary = psddf.ymaze.correct %>%
  filter(learning_day != 4)  %>%
  group_by(animal, laserOn, stage_desc, channelLocation) %>% 
  dplyr::summarise(swr_incidence.mean=mean(swr_incidence),
                   swr_incidence.sem=sem(swr_incidence),
                   has_ripples.pct=sum(swr_incidence > 0) / n(),
                   nripples.mean = mean(nripples)) 
#swr.ymaze.summary$date = as.factor(swr.ymaze.summary$date)
```

```{r}
swr.ymaze.summary %>%
  filter(stage_desc == 'DuringStim')  %>%
  #dplyr::mutate(date_animal = paste(format(date), animal, sep='_'),
  #              date_laser_val = as.numeric(date) + (as.numeric(laserOn) - 1) * 0.5 - 0.25) %>% 
  ggplot() +
  #geom_point(aes(x=laserOn, y=swr_incidence.mean, color=animal)) +
  geom_line(aes(x=laserOn, y=swr_incidence.mean, group=animal)) +
  geom_ribbon(aes(x=laserOn, 
                  ymin=swr_incidence.mean - swr_incidence.sem, 
                  ymax=swr_incidence.mean + swr_incidence.sem,
                  group=animal), 
                alpha=0.1) +
  xlab('Stimulation') + ylab('Ripple incidence at goal (Hz)') +
  facet_grid(. ~ channelLocation) +
  scale_x_discrete(labels=c('off', 'on')) +
  scale_y_continuous(breaks=c(0, 0.1, 0.2)) +
  #scale_x_continuous(breaks=c(5,6))+
  gtheme

ggsave(paste0(img_dir, '/ripples_change.pdf'), units = 'cm',
       dpi=300, device=cairo_pdf,
       height=5, width=4.5)
```

```{r}
swr.ymaze.summary %>% 
  filter(stage_desc == 'DuringStim')  %>%
  DT::datatable()

psddf.ymaze.correct %>%
  filter(stage_desc == 'DuringStim')  %>%
  dplyr::select(date, animal, trial, laserOn, swr_incidence, nripples) %>%
  DT::datatable()
```
Significance testing
```{r}
tested.ymaze.correct = filter(psddf.ymaze.correct, 
                              learning_day != 4, # Exclude the day when laser was turned off.
                              #laserOn == 0,
                              channelLocation == 'CA1',
                              stage_desc == 'DuringStim') %>%
  dplyr::mutate(early.learning=(learning_day < 5))
# Count of trials per animal
tested.ymaze.correct %>% group_by(animal, channelLocation, laserOn) %>%
  dplyr::summarise(n=n()) %>%
  group_by(laserOn) %>% 
  dplyr::summarise(mean(n), sem(n))

tested.ymaze.correct %>% group_by(laserOn) %>%
  dplyr::summarise(mean(swr_incidence), sem(swr_incidence))

m.full = lmerTest::lmer(swr_incidence ~ laserOn + (1 + laserOn | animal), 
                        data=tested.ymaze.correct, 
                        REML = TRUE) 
plot.model.diagnostics(m.full, tested.ymaze.correct$animal, tested.ymaze.correct$early.learning) 
summary(m.full)
coef(m.full)$animal
anova(m.full, refit=FALSE, ddf='Satterthwaite')
```


