---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Script run after ymaze_ripples.Rmd

```{r include=FALSE}
knitr::opts_chunk$set(include=TRUE, collapse=TRUE, warning=FALSE, echo=FALSE)
```

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)
library(ggpubr)
library(plotly)
library(purrr)
select = dplyr::select

source('laser_stats.R')
source('plotting_params.R')
source('psd_analysis.R')
source('psd_fitting.R')
```

```{r}
img_dir = '/home/prez/tmp/ymaze_chat_x_ai32/img_gen/ymaze'
data_dir =  '/mnt/DATA/chat_ripples/y-maze'
diode.signal = TRUE
min.stim.stage.dur.sec = 10

trial.info.df = read_csv(paste(data_dir, 'trials.csv', sep='/')) %>%
  dplyr::mutate(file_name=paste0('signal/', animal, '_trial_', trial, '_g0'))
trial.info.df$date = as.Date(trial.info.df$date, '%d/%m/%Y')

freq.bands.df = data.frame(
  band=c('theta', 'slow gamma'),
  xmin=c(5, 25),
  #xmax=c(9, 45)
  xmax=c(12,45)
)
```

Load z-scored Morlet PSD estimate data for the task stage effects
```{r}
if (diode.signal) {
  input.filename = 'morlet_psd_table_diode_th7.csv'
} else {
  input.filename = 'morlet_psd_table_th7.csv'
}

psddf.ymaze = bind_rows(
  read_csv(file.path(data_dir, 'trial_results', input.filename)) %>% dplyr::mutate(exp='main-effect'),
  read_csv(file.path(data_dir, 'trial_results_gfp', input.filename)) %>% dplyr::mutate(exp='gfp-control'))
psddf.ymaze = prepare.ymaze.df(psddf.ymaze)
psddf.ymaze = left_join(psddf.ymaze, dplyr::select(trial.info.df, -trial, -state, -laserOn), 
                        by=c('date', 'animal', 'file_name', 'exp')) %>%
  dplyr::mutate(exp_animal = paste(exp, animal, sep='_'))

band.zscore = melt.freq.bands(filter(psddf.ymaze, correct==1), 
                             extra.id.vars=c('learning_day', 'dirname', 'exp', 'exp_animal'),
                             psd.vars.prefix='all_psd_z_',
                             freq.bands = c(exp(seq(0.1, 5.6, by=0.07)))) %>%
  dplyr::rename(band.zscore=band_power)
```

Load Welch's PSD estimate data
```{r}
if (diode.signal) {
  input.filename = 'welch_psd_table_diode_th7.csv'
} else {
  input.filename = 'welch_psd_table_th7.csv'
}
psddf.ymaze = bind_rows(
  read_csv(file.path(data_dir, 'trial_results', input.filename)) %>% dplyr::mutate(exp='main-effect'),
  read_csv(file.path(data_dir, 'trial_results_gfp', input.filename))  %>% dplyr::mutate(exp='gfp-control'))

psddf.ymaze = prepare.ymaze.df(psddf.ymaze)
psddf.ymaze = left_join(psddf.ymaze, dplyr::select(trial.info.df, -trial, -state, -laserOn), 
                        by=c('date', 'animal', 'file_name', 'exp')) %>%
  dplyr::mutate(exp_animal = paste(exp, animal, sep='_'))
#psddf.ymaze = filter(psddf.ymaze, channelLocation == 'CA1')

psddf.ymaze = filter(psddf.ymaze, !(exp_animal %in% excluded.swr.exp_animals))

psd.molten = melt.freq.bands(filter(psddf.ymaze, correct==1), 
                             extra.id.vars=c('learning_day', 'dirname', 'exp', 'exp_animal', 'noise_dur_sec', 'stage_dur_sec'),
                             psd.vars.prefix='all_psd_xx_')
```

# Differences in PSD between stages
```{r}
axis.breaks=c(1:9,seq(10,100,10), 200)
axis.labels=rep('', length(axis.breaks))
axis.labels[1]=1
axis.labels[10]=10
axis.labels[19]=100

band.zscore %>%
  filter(laserOn == 0) %>%
  filter(animal == 'BS') %>%
  filter(learning_day == 6)  %>%
  filter(stage_desc %in% c('MazeStem', 'DuringStim')) %>%
  #filter(stage_desc %in% c('DuringStim')) %>%
  dplyr::mutate(trial_stage = paste0(trial_id, stage_desc, sep='_')) %>% 
  ggplot(aes(x=band_start_freq, y=band.zscore, group=trial_stage, color=stage_desc)) +
  geom_line(size=0.5*px2pt)  +
  facet_grid(laserOn ~ channelLocation) +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  geom_hline(yintercept = 0.0, linetype='dashed') +
  gtheme
```

```{r}
animal.band.zscore = band.zscore %>%
  filter(stage_desc %in% c('MazeStem', 'DuringStim')) %>%
  filter(learning_day == 6)  %>%
  group_by(animal, exp, exp_animal, channelLocation, laserOn, stage_desc, band_start_freq) %>%
  dplyr::summarise(mean.zscore = mean(band.zscore),
                   sem.zscore = sem(band.zscore))

g.stage.band.zscore = animal.band.zscore %>%
  filter(laserOn == 0) %>%
  filter(exp=='main-effect', channelLocation == 'CA1') %>%
  #filter(animal == 'BS') %>%
  filter(animal == 'BS') %>%
  ggplot(aes(x=band_start_freq, y=mean.zscore, group=stage_desc)) +
  geom_line(aes(color=stage_desc), size=1*px2pt) +
  geom_ribbon(aes(ymin=mean.zscore - sem.zscore, ymax=mean.zscore + sem.zscore), alpha=0.2) +
  geom_hline(yintercept = 0.0, linetype='dashed') +
  gtheme +
  coord_flip() +
  facet_grid(laserOn ~ channelLocation) +
  #ylim(-1, 1.75) +
  #ylim(-1, 1.8) +
  xlab('Frequency (Hz)') +
  ylab('Power z-score') 

g.stage.band.zscore.lowfreq = g.stage.band.zscore + xlim(2,15)
g.stage.band.zscore.highfreq = g.stage.band.zscore + xlim(14, 250)
plot_grid(g.stage.band.zscore.highfreq, g.stage.band.zscore.lowfreq, ncol=1, rel_heights = c(3,2))
ggsave(paste0(img_dir, '/psd_zscore_giht.pdf'), units = 'cm',
       dpi=300, device=cairo_pdf,
       height=11, width=10)
```

# Effect of the stage on PSD
```{r}
animal.psd = psd.molten %>%
  group_by(animal, exp, exp_animal, learning_day, channelLocation, laserOn, stage_desc, band_start_freq) %>%
  dplyr::summarise(mean.power = mean(log(band_power)),
                   sem.power = sem(log(band_power)))
```

```{r}
noisy_psd_trials = c('2019-11-13_OS_signal/OS_trial_6_g0_2',
                     '2019-11-06_BS_signal/BS_trial_4_g0_2',
                     '2019-11-07_BS_signal/BS_trial_2_g0_2')
psd.molten %>%
  filter(channelLocation == 'CA1', stage_desc == 'DuringStim', stage_dur_sec >= 10) %>%
  filter(!(trial_id %in% c(noisy_psd_trials))) %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, group=trial_id, y=log(band_power), colour=laserOn), width=0.5) + 
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-20, ymax=5, alpha=0.05, fill='grey10') +
  scale_x_log10(limits=c(2,200), breaks=axis.breaks, labels=axis.labels) +
  facet_wrap(exp + animal ~ ., ncol = 4, scales = 'free') +
  xlab('Frequency (Hz)') +
  ylab('Log power change') +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  theme(legend.position = 'right') +
  gtheme -> g

ggplotly(g)
```


```{r}
animal.psd %>%
  filter(laserOn == 0) %>%
  filter(learning_day==6) %>%
  filter(stage_desc %in% c('MazeStem', 'DuringStim')) %>%
  ggplot(aes(x=band_start_freq, y=mean.power, group=stage_desc)) +
  geom_line(aes(color=stage_desc), size=2*px2pt) +
  geom_ribbon(aes(ymin=mean.power - sem.power, ymax=mean.power + sem.power), alpha=0.2) +
  facet_grid(exp + animal ~ channelLocation) +
  scale_x_log10(limits=c(2,250), breaks=axis.breaks, labels=axis.labels) +
  geom_hline(yintercept = 0.0, linetype='dashed') +
  gtheme +
  xlab('Frequency (Hz)') +
  ylab('Power z-score') 
```

PSD diff
```{r}
psd.dayaverage = psd.molten %>%
  filter(stage_desc == 'DuringStim', stage_dur_sec >= min.stim.stage.dur.sec) %>%
  filter(!(trial_id %in% c(noisy_psd_trials))) %>%
  group_by(animal, date, channelLocation, laserOn, learning_day, exp, exp_animal, band_name) %>%
  dplyr::summarise(band_start_freq=mean(band_start_freq),
                   band_power.mean=mean(band_power),
                   band_power.sem=sem(band_power),
                   n=n())

psd.daydiff = reshape2::dcast(psd.dayaverage,
                  animal + date + channelLocation + learning_day + exp + exp_animal + band_name + band_start_freq ~ laserOn,
                  value.var = 'band_power.mean') %>% 
    dplyr::mutate(logpower.diff = log(`1`) - log(`0`)) %>%
    filter(!is.na(logpower.diff))

psd.daydiff %>%
  filter(channelLocation == 'CA1') %>%
  ggplot() +
  geom_line(aes(x=band_start_freq, group=date, y=logpower.diff, colour=exp), width=0.5) + 
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-3, ymax=5, alpha=0.05, fill='grey10') +
  scale_x_log10(limits=c(2,200), breaks=axis.breaks, labels=axis.labels) +
  geom_hline(yintercept=0, linetype='dashed') +
  facet_wrap(exp + animal ~ ., ncol = 4, scales='free_x') +
  xlab('Frequency (Hz)') +
  ylab('Log power change') +
  scale_color_manual(values=expPalette) +
  theme(legend.position = 'right') +
  gtheme -> g
ggplotly(g)
```

Day-averaged Plot
```{r}
animal.psd.daydiff = psd.daydiff %>%
  dplyr::group_by(band_name, band_start_freq, channelLocation, exp, animal) %>%
  dplyr::summarise(logpower.diff.mean=mean(logpower.diff, na.rm=TRUE),
                   logpower.diff.sem=sem(logpower.diff))
  
animal.psd.daydiff %>%
  filter(channelLocation == 'CA1') %>%
  ggplot() +
  geom_ribbon(aes(x=band_start_freq, ymin=logpower.diff.mean-logpower.diff.sem, ymax=logpower.diff.mean+logpower.diff.sem),
              alpha=0.25) +
  geom_line(aes(x=band_start_freq, y=logpower.diff.mean, colour=exp), width=0.5) + 
  #geom_rect(data=all.freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band, fill=band), 
  #          ymin=-3, ymax=5, alpha=0.05) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
          ymin=-1, ymax=1.2, alpha=0.05, fill='grey10') +
  scale_x_log10(limits=c(2,200), breaks=axis.breaks, labels=axis.labels) +
  geom_hline(yintercept=0, linetype='dashed') +
  facet_wrap(exp + animal ~ ., ncol = 4, scales = 'free_x') +
  xlab('Frequency (Hz)') +
  ylab('Log power change') +
  scale_color_manual(values=expPalette) +
  theme(legend.position = 'right') +
  gtheme
ggsave(file=paste0(img_dir, '/', '3_psd_diff.pdf'), 
       width=15, height=9, unit='cm', dpi=300, device=cairo_pdf)
```
Statistics on logpower differences per band
```{r}
all.freq.bands.df = data.frame(
  band=c('slow', 'supra_theta', 'pre_slow_gamma', 'supra_slow_gamma'),
  xmin=c(3.5, 12, 15, 90),
  xmax=c(5, 15, 20, 110)
) %>% bind_rows(freq.bands.df) %>%
  dplyr::arrange(xmin)
rownames(all.freq.bands.df) = all.freq.bands.df$band

get.band.name = function(freq) {
  band_ind = which(freq <= all.freq.bands.df$xmax & freq > all.freq.bands.df$xmin)
  if (length(band_ind) > 0) {
    return(as.character(all.freq.bands.df$band[band_ind]))
  } else {
    return('ignored')
  }
}
```

Minimum and maximum difference per freq band
```{r warning=FALSE}
band.logpower.diff = psd.daydiff %>%
  dplyr::mutate(band_name = map_chr(band_start_freq, get.band.name)) %>% 
  group_by(exp, animal, exp_animal, date, learning_day, channelLocation, band_name) %>%
  dplyr::summarise(min.band.logpower.diff = min(logpower.diff, na.rm=TRUE),
                   max.band.logpower.diff = max(logpower.diff, na.rm=TRUE)) %>%
  filter(!is.infinite(min.band.logpower.diff), !is.infinite(max.band.logpower.diff)) %>% # skip trials when NA for logpower.diff
  dplyr::mutate(exp_animal = paste(exp, animal, sep='_'))

band.logpower.diff$band_name = factor(band.logpower.diff$band_name, levels=c(as.character(all.freq.bands.df$band), 'ignored'))
```

```{r}
band.relative.diff = band.logpower.diff %>%
  dplyr::mutate(band.logpower.diff = max.band.logpower.diff) %>%
                  #ifelse(band_name %in% c('theta', 'slow_gamma'), max.band.logpower.diff, min.band.logpower.diff)) %>% 
  reshape2::dcast(
   animal + date + learning_day + channelLocation + exp + exp_animal ~ band_name,
   value.var = 'band.logpower.diff') %>% 
   dplyr::mutate(theta_above_slow = theta - slow, 
                 theta_above_supra = theta - supra_theta,
                 slow_gamma_above_supra_theta = `slow gamma` - pre_slow_gamma,
                 slow_gamma_above_supra = `slow gamma` - supra_slow_gamma) %>% 
  dplyr::select(-c(theta, slow, supra_theta, `slow gamma`, supra_slow_gamma, pre_slow_gamma, ignored)) %>%
  reshape2::melt(id.vars = c('animal', 'date', 'learning_day', 'channelLocation', 'exp', 'exp_animal'), 
                 variable.name='compared.bands',
                 value.name='relative.diff') 

band.relative.diff %>%
  filter(channelLocation == 'CA1') %>%
  ggplot(aes(x=exp, y=relative.diff, text=paste(exp, animal, date, relative.diff))) +
  geom_jitter(aes(color=exp), shape=1, width=0.25, height=0, alpha=0.5, size=0.5, stroke=0.5) +
  geom_hline(yintercept=0, linetype='dashed') +
  facet_wrap(compared.bands ~ ., ncol=4) +
  scale_color_manual(values=expPalette) +
  #ylim(c(-0.8, 1.6)) +
  gtheme +
  xlab('') + ylab('Relative difference in change') ->
  g
ggplotly(g, tip='text')
ggsave(file=paste0(img_dir, '/', '3_psd_diff_stat.pdf'), 
       width=10, height=5.5, unit='cm', dpi=300, device=cairo_pdf)


band.relative.diff %>%
  filter(channelLocation == 'CA1') %>% 
  dplyr::ungroup() %>%
  dplyr::select(exp, animal, learning_day, compared.bands, relative.diff) %>%
  write.csv(file.path(img_dir, 'Figure3 - figure supplement2 - Source Data - PSD change per freq band.csv'))
```

```{r}
tested.df = filter(band.relative.diff, channelLocation == 'CA1', 
                                    #compared.bands == 'theta_above_slow')
                                    #compared.bands == 'theta_above_supra')
                                    #compared.bands == 'slow_gamma_above_supra')
                                    compared.bands == 'slow_gamma_above_supra_theta')
m.full = lmerTest::lmer(relative.diff ~ exp + (1 + exp | exp_animal), 
                        data=tested.df,
                        REML = TRUE) 
summary(m.full)
anova(m.full, refit=FALSE, ddf='Satterthwaite')
plot.model.diagnostics(m.full, tested.df$animal, tested.df$exp)
residuals(m.full) %>% shapiro.test()
```


# Laser effect on PSD at Goal
```{r}
animals.psd = psd.molten %>%
  #filter(learning_day >= 5)  %>%
  #filter(animal == 'OS') %>%
  filter(stage_desc %in% c('DuringStim')) %>%
  filter(!(trial_id %in% c(noisy_psd_trials))) %>%
  group_by(exp, animal, exp_animal, channelLocation, laserOn, stage_desc, band_start_freq) %>%
  dplyr::summarise(sem.power = sem(log(band_power)),
                   band_power = mean(log(band_power)))
```


```{r include=FALSE}
joined.psd.fit.df = map_dfr(unique(animals.psd$exp_animal), ~ {
  animal.psd = filter(animals.psd, exp_animal == .x)
  animal.psd$name = 'model'
  animal.fit.low.freq = calc.animal.band.fit.df(animal.psd, c(2.5, 20), max.npeaks=1) %>%
    dplyr::mutate(animal = animal.psd$animal[1], exp = animal.psd$exp[1], name = paste(name, 'low_freq', sep='_'))
  animal.fit.high.freq = calc.animal.band.fit.df(animal.psd, c(15, 150)) %>%
    dplyr::mutate(animal = animal.psd$animal[1], exp = animal.psd$exp[1], name = paste(name, 'high_freq', sep='_'))
  bind_rows(animal.psd, animal.fit.low.freq, animal.fit.high.freq)
})
```

```{r}
ca1.psd.fit.df = filter(joined.psd.fit.df, channelLocation != 'CA3') %>%
  dplyr::mutate(name_laser=paste(name, laserOn, sep='_'))
ca1.psd.fit.df %>%
  ggplot() +
  geom_ribbon(aes(x=band_start_freq, y=band_power, 
              group=name_laser, fill=laserOn,
              ymin=band_power - sem.power, ymax=band_power + sem.power), 
          alpha=0.8) +
  geom_line(data=filter(ca1.psd.fit.df, name != 'model'), aes(x=band_start_freq, y=band_power, 
              group=name_laser, color=laserOn, linetype=name)) +
  geom_rect(data=freq.bands.df, mapping=aes(xmin=xmin, xmax=xmax, group=band), 
            ymin=-20, ymax=-5, alpha=0.05, fill='grey10') +
  facet_wrap(exp + animal ~ ., scales = 'free', ncol = 4) +
  scale_x_log10(limits=c(2,200), breaks=axis.breaks, labels=axis.labels) +
  scale_color_manual(values = c(nolaser.col, laser.col)) +
  scale_fill_manual(values = c(nolaser.col, laser.col)) +
  gtheme +
  theme(legend.position = 'none') +
  scale_linetype_manual(values=c('dotted', 'dotted', 'solid')) +
  xlab('Frequency (Hz)') + ylab('Log power')

ggsave(file=paste0(img_dir, '/', '5_ymaze_psd_mean_all.pdf'), 
       width=15, height=9, unit='cm', dpi=300, device=cairo_pdf)
```

# PSD fit
Fit background with FOOOF and check quality
```{r}
fit.psd.ymaze.high = fit.background.df(
  filter(psd.molten,
         channelLocation == 'CA1',
         stage_desc == 'DuringStim',
         stage_dur_sec - noise_dur_sec >= min.stim.stage.dur.sec,
         !(trial_id %in% c(noisy_psd_trials))),
  freq.bands.df,
  freq.range = c(15, 150),
  fit.knee = FALSE,
  show.fit = FALSE,
  max.npeaks = 8,
  extra.group.vars = c('exp_animal'))

summary(fit.psd.ymaze.high$fit_error)
fit.psd.ymaze.high$correct = 1
```

```{r}
plot.laser.change(fit.psd.ymaze.high, background_auc) + ylab('Background spectrum AUC')
ca1.bac.df = filter(fit.psd.ymaze.high, channelLocation == 'CA1') 
dplyr::select(ca1.bac.df, exp, animal, trial_id, laserOn, background_auc) %>%
  write.csv(file.path(img_dir, 'Figure 3H - Source Data - Aperiodic component 15-150 Hz.csv'))
bac.auc.model = calc.laser.fixed.effects(
  ca1.bac.df, 
  background_auc)

g.bac.auc.high = plot.samples(ca1.bac.df, background_auc) + 
  ylab('AUC')
g.bac.auc.high
```


## Slow gamma
```{r}
var = quo(pow_slow_gamma)

pct.sgamma.oscillating = group_by(fit.psd.ymaze.high, channelLocation, exp, animal, exp_animal, laserOn) %>%
  dplyr::summarise(pct.oscillating=sum(!is.na(!!var)) / n(), n())
group_by(pct.sgamma.oscillating, channelLocation, laserOn) %>% dplyr::summarise(mean(pct.oscillating), sem(pct.oscillating))

fit.sgamma.present = filter(fit.psd.ymaze.high) %>%
  dplyr::filter(!is.na(!!var))

dplyr::select(fit.sgamma.present, exp, animal, trial_id, laserOn, pow_slow_gamma) %>%
  write.csv(file.path(img_dir, 'Figure 3G - Source Data - Slow Gamma Power.csv'))

group_by(fit.sgamma.present, channelLocation, exp, laserOn) %>%
  dplyr::summarise(mean(!!var), sem(!!var), n())

plot.laser.change(fit.sgamma.present, !!var) + ylab('Relative Slow Gamma Power (20 - 45 Hz)')
sgamma.model = calc.laser.fixed.effects(subset(fit.sgamma.present, channelLocation == 'CA1'), !!var)
g.sgamma.pow = plot.samples(subset(fit.sgamma.present, channelLocation == 'CA1'), !!var) +
  ylab('Relative Slow Gamma Power (20 - 45 Hz; a.u.)')
#g.sgamma.pow

ggplotly(g.sgamma.pow)
```

Slow gamma peak frequency
```{r}
var = quo(peak_slow_gamma)

group_by(fit.sgamma.present, channelLocation, exp, laserOn) %>%
  dplyr::summarise(mean(!!var), sem(!!var), n())

plot.laser.change(fit.sgamma.present, !!var) + ylab('Slow Gamma Peak (20 - 45 Hz)')
sgamma.model = calc.laser.fixed.effects(subset(fit.sgamma.present, channelLocation == 'CA1'), (!!var))
g.sgamma.peak = plot.samples(subset(fit.sgamma.present, channelLocation == 'CA1'), !!var) +
  ylab('Slow Gamma Peak frequency')
g.sgamma.peak
```


## Theta
Fit background with FOOOF and check quality
```{r}
fit.psd.ymaze.low = fit.background.df(
  filter(psd.molten,
         channelLocation=='CA1',
         stage_desc == 'DuringStim',
         stage_dur_sec - noise_dur_sec >= min.stim.stage.dur.sec,
         !(trial_id %in% c(noisy_psd_trials))),
  freq.bands.df,
  show.fit=FALSE,
  freq.range = c(3.5, 15),
  max.npeaks = 1,
  fit.knee = FALSE,
  extra.group.vars = c('exp_animal'))

summary(fit.psd.ymaze.low$fit_error)
summary(fit.psd.ymaze.low$r_squared)
fit.psd.ymaze.low$correct = 1
```

Count of trials with theta:
```{r}
var = quo(pow_theta)
pct.theta.oscillating = group_by(fit.psd.ymaze.low, channelLocation, exp, animal, exp_animal, laserOn) %>%
  dplyr::summarise(pct.oscillating=sum(!is.na(!!var)) / n())
pct.theta.oscillating
ca.subset = subset(pct.theta.oscillating, channelLocation == 'CA1')
t.test(subset(ca.subset, laserOn==0)$pct.oscillating,
       subset(ca.subset, laserOn==1)$pct.oscillating, 
       paired=TRUE)
group_by(pct.theta.oscillating, channelLocation, laserOn) %>% dplyr::summarise(mean(pct.oscillating), sem(pct.oscillating))
```

Change in pow theta.
```{r}
var = quo(pow_theta)
fit.theta.present = filter(fit.psd.ymaze.low) %>%
  dplyr::filter(!is.na(!!var)) 

plot.laser.change(fit.theta.present, !!var) + ylab('Relative Theta Power (5 - 12 Hz)')

group_by(fit.theta.present, channelLocation, laserOn) %>%
  dplyr::summarise(mean(!!var), sem(!!var))

dplyr::select(fit.theta.present, exp, animal, trial_id, laserOn, pow_theta) %>%
  write.csv(file.path(img_dir, 'Figure 3E - Source Data - Theta Power.csv'))

m.full = calc.laser.fixed.effects(subset(fit.theta.present, channelLocation == 'CA1'), pow_theta)
g.theta.pow = plot.samples(subset(fit.theta.present, channelLocation == 'CA1'), pow_theta) +
  ylab('Relative theta power (5 - 12 Hz)')
g.theta.pow
ggplotly(g.theta.pow)
```

Reduced background spectrum in low frequency bands
```{r}
var = quo(background_auc)

group_by(fit.theta.present, channelLocation, exp, laserOn) %>%
  dplyr::summarise(mean(!!var), sem(!!var))

m.full = calc.laser.fixed.effects(subset(fit.theta.present, channelLocation == 'CA1'), !!var)
g.bac.auc.low = plot.samples(subset(fit.theta.present, channelLocation == 'CA1'), !!var) +
  ylab('AUC')
g.bac.auc.low
#g.theta.peak
ggplotly(g.bac.auc.low)
```

Theta peak
```{r}
var = quo(peak_theta)
fit.theta.present = filter(fit.psd.ymaze.low) %>%
  dplyr::filter(!is.na(!!var)) 

plot.laser.change(fit.theta.present, !!var) + ylab('Theta Peak (Hz)')

group_by(fit.theta.present, channelLocation, exp, laserOn) %>%
  dplyr::summarise(mean(!!var), sem(!!var))
dplyr::select(fit.theta.present, exp, animal, trial_id, laserOn, peak_theta) %>%
  write.csv(file.path(img_dir, 'Figure 3F - Source Data - Theta peak freq.csv'))

m.full = calc.laser.fixed.effects(subset(fit.theta.present, channelLocation == 'CA1'), !!var)
g.theta.peak = plot.samples(subset(fit.theta.present, channelLocation == 'CA1'), !!var) +
  ylab('Theta peak (5 - 12 Hz)')
g.theta.peak
ggplotly(g.theta.peak)
```

## Save plot with stats
```{r}
plot_grid(g.bac.auc.low, g.bac.auc.high, g.theta.pow, g.theta.peak, g.sgamma.pow, ncol=5)
ggsave(file=paste0(img_dir, '/', '5_psd_stats.pdf'), 
       width=18, height=5, unit='cm', dpi=300, device=cairo_pdf)
```

